---
title: "snTC Final Code AZ"
output: html_document
date: "2025-06-25"
---

# Set Working Directory
```{r setup, include=FALSE}
setwd("~/apps/snTC/15k_RPCA_20240903_Drop24B/20241231_Cluster_split_data")
```
Load Necessary Libraries


```{r Load packages and set up the environment; message = FALSE; warning = FALSE}
library(readr)
library(dplyr)
library(tidyr)
library(DESeq2, lib.loc = "/panfs/jay/groups/18/greenham/azulfiqa/R/4.4.0")
library(genefilter, lib.loc = "/panfs/jay/groups/18/greenham/azulfiqa/R/4.4.0")
library(ggplot2)
library(readxl)
```

Function to process the clusters 

```{r}
process_cluster <- function(cluster_number) {
  # Initialize an empty list to store results
  result_list <- list()
  
  # Define your grouping factor
  group <- factor(c(rep(1:6, each = 2), 7))
  
  # Loop through all sample files
  for (i in 1:13) {
    # Construct the file path
    file_path <- paste0("20241231.snTC.RPCA15k.DROPZT24B.sample", i, "cluster", cluster_number, ".counts.csv")
    
    # Read the file
    cluster_data <- read_csv(file_path)
    
    # Convert relevant columns to numeric
    cluster_numeric <- cluster_data %>%
      mutate(across(-1, as.numeric))
    
    # Extract the name of the first column
    first_column_name <- names(cluster_numeric)
    
    # Calculate row sums
    sums_vector <- rowSums(cluster_numeric[, -1], na.rm = TRUE)
    
    # Create a data frame with gene names, sum vector, and column name
    result_df <- data.frame(
      gene = cluster_numeric[[first_column_name]],
      Cluster = paste0("Cluster", cluster_number, "_ZT", i),
      sum = sums_vector
    )
    
    # Append the result to the list
    result_list[[i]] <- result_df
  }
  
  # Combine the results into a single data frame
  final_result_df <- do.call(rbind, result_list)
  
  # Pivot the data
  wide_data <- final_result_df %>%
    pivot_wider(names_from = Cluster, values_from = sum)
  
  # Prepare data for DESeq2
  counts_matrix <- as.matrix(wide_data[, -1])
  rownames(counts_matrix) <- wide_data$gene
  meta_df <- data.frame(row.names = colnames(counts_matrix), Type = group)
  
  # Create DESeq2 dataset
  dds <- DESeqDataSetFromMatrix(countData = round(counts_matrix),
                                 colData = meta_df,
                                 design = ~Type)
  
  # Run the DESeq2 normalization
  dds <- DESeq(dds)
  
  # Apply the variance-stabilizing transformation
  vsd <- varianceStabilizingTransformation(dds)
  
  # Extract the normalized data
  expr_normalized <- assay(vsd)
  
  # Convert normalized data to a data frame and add gene names
  expr_normalized_df <- data.frame(expr_normalized) %>%
    mutate(Gene_id = rownames(expr_normalized))
  
  # Write the normalized data to a CSV file
  write.csv(expr_normalized_df, 
            paste0("/home/greenham/azulfiqa/apps/snTC/15k_RPCA_20240903_Drop24B/20241231_Cluster_split_data/DeSeq2_Normalized_Counts/Cluster", cluster_number, "_ZTs_normalized_counts.csv"), 
            row.names = TRUE)
  
  # Optional: Visualize normalized expression
  expr_normalized_df_long <- expr_normalized_df %>%
    pivot_longer(-Gene_id, names_to = "Sample", values_to = "Expression")
  
  plot <- expr_normalized_df_long %>%
    ggplot(aes(x = Sample, y = Expression)) +
    geom_violin() +
    geom_point() +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90)) +
    ylim(0, NA) +
    labs(title = paste("Normalized Expression for Cluster", cluster_number),
         x = "Sample",
         y = "Normalized Expression")
  
  print(plot)
}

# Process Clusters 0 to 18
for (cluster_number in 0:18) {process_cluster(cluster_number)}
```
MetaCycle Analysis

```{r}
library(MetaCycle)

# Set input and output directories
input_directory <- "/home/greenham/azulfiqa/apps/snTC/15k_RPCA_20240903_Drop24B/20241231_Cluster_split_data/DeSeq2_Normalized_Counts/"
output_directory <- "/panfs/jay/groups/18/greenham/azulfiqa/apps/snTC/15k_RPCA_20240903_Drop24B/20241231_Cluster_split_data/DeSeq2_Normalized_Counts/MetacycleDeSeq_Normalised_Cluster/"

# Loop through clusters for MetaCycle analysis
for (i in 0:18) {
  # Construct the file paths
  input_file <- paste0(input_directory, "Cluster", i, "_ZTs_normalized_counts.csv")
  output_file <- paste0(output_directory, "Cluster", i, "_Counts_Compiled_All_ZTs.csv")
  
  # Read the cluster file
  cluster_data <- read_csv(input_file)
  
  # Extract gene names
  genes <- cluster_data$gene
  
  # Modify column names
  new_header <- c("Gene", rep(seq(0, 24, by = 4), each = 2), 24)
  colnames(cluster_data) <- new_header
  
  # Write the modified data to a new CSV file
  write.csv(cluster_data, file = output_file, row.names = FALSE)
  
  # Run the meta2d command if needed
  meta2d(infile = output_file, filestyle = "csv", outdir = output_directory,
         timepoints = "Line1")
}
```
WGCNA_Analysis 
```{r}
setwd("~/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster")
```

List of File Names to get normalised expression for all genes in all clusters

```{r}
file_names <- c("Cluster0_Counts_Compiled_All_ZTs.csv",
                 "Cluster1_Counts_Compiled_All_ZTs.csv",
                 "Cluster2_Counts_Compiled_All_ZTs.csv",
                 "Cluster3_Counts_Compiled_All_ZTs.csv",
                 "Cluster4_Counts_Compiled_All_ZTs.csv",
                 "Cluster5_Counts_Compiled_All_ZTs.csv",
                 "Cluster6_Counts_Compiled_All_ZTs.csv",
                 "Cluster7_Counts_Compiled_All_ZTs.csv",
                 "Cluster8_Counts_Compiled_All_ZTs.csv",
                 "Cluster9_Counts_Compiled_All_ZTs.csv",
                 "Cluster10_Counts_Compiled_All_ZTs.csv",
                 "Cluster11_Counts_Compiled_All_ZTs.csv",
                 "Cluster12_Counts_Compiled_All_ZTs.csv",
                 "Cluster13_Counts_Compiled_All_ZTs.csv",
                 "Cluster14_Counts_Compiled_All_ZTs.csv",
                 "Cluster15_Counts_Compiled_All_ZTs.csv",
                 "Cluster16_Counts_Compiled_All_ZTs.csv",
                 "Cluster17_Counts_Compiled_All_ZTs.csv",
                 "Cluster18_Counts_Compiled_All_ZTs.csv")
```
Initialize an Empty List to Store the Data Frames
```{r}
all_matrices <- list()
```

Loop Through Each File to Read and Store the Data Frames

```{r}
for (file in file_names) {
  # Read the matrix data from the CSV file
  matrix_data <- read_csv(file)

  # Extract the cluster number from the file name
  cluster_number <- sub(".*Cluster([0-9]+).*", "\\1", file)

  # Add the cluster number to the gene IDs
  matrix_data <- matrix_data %>%
    mutate(Gene = paste0(Gene, "_", cluster_number))

  # Store the data frame in the list
  all_matrices <- append(all_matrices, list(matrix_data))
}
```

Optionally, Combine All Data Frames into One
```{r}
combined_df <- bind_rows(all_matrices)

# Set new column names
new_header <- c("Gene", "ZT0A", "ZT0B", "ZT04A", "ZT04B", "ZT08A", "ZT08B", 
                "ZT12A", "ZT12B", "ZT16A", "ZT16B", "ZT20A", "ZT20B", "ZT24A", "ZT24B")
colnames(combined_df) <- new_header

# View the combined data frame
print(head(combined_df))

# Write the combined data frame to a CSV file
write.csv(combined_df, "Combined_ZTs_DeSeq_normalized_counts_matrix.csv", row.names = FALSE)
```

Make one matrix for 0.05p sorted cyclic genes and merge with Combined_ZTs_DeSeq_normalized_counts_matrix.csv to feed to WGCNA 
```{r}
Cluster0 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster0_0.05.xlsx")
Cluster1 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster1_0.05.xlsx")
Cluster2 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster2_0.05.xlsx")
Cluster3 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster3_0.05.xlsx")
Cluster4 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster4_0.05.xlsx")
Cluster5 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster5_0.05.xlsx")
Cluster6 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster6_0.05.xlsx")
Cluster7 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster7_0.05.xlsx")
Cluster8 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster8_0.05.xlsx")
Cluster9 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster9_0.05.xlsx")
Cluster10 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster10_0.05.xlsx")
Cluster11 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster11_0.05.xlsx")
Cluster12 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster12_0.05.xlsx")
Cluster13 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster13_0.05.xlsx")
Cluster14 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster14_0.05.xlsx")
Cluster15 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster15_0.05.xlsx")
Cluster16 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster16_0.05.xlsx")
Cluster17 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster17_0.05.xlsx")
Cluster18 <- read_excel("/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data/Cluster18_0.05.xlsx")


# List of file names and their corresponding suffixes
file_info <- list(
  Cluster0 = "0",
  Cluster1 = "1",
  Cluster2 = "2",
  Cluster3 = "3",
  Cluster4 = "4",
  Cluster5 = "5",
  Cluster6 = "6",
  Cluster7 = "7",
  Cluster8 = "8",
  Cluster9 = "9",
  Cluster10 = "10",
  Cluster11 = "11",
  Cluster12 = "12",
  Cluster13 = "13",
  Cluster14 = "14",
  Cluster15 = "15",
  Cluster16 = "16",
  Cluster17 = "17",
  Cluster18 = "18"
)

#read in files with genes name for each cluster

# Initialize an empty list to store the data frames
all_matrices <- list()

# Loop through each file and its corresponding suffix
for (cluster_name in names(file_info)) {
  # Construct the file path
  file_path <- paste0(cluster_name, ".xlsx")
  
  # Read the data from the file
  cluster_data <- read_excel(file_path)
  
  # Add the suffix to the 'Gene' column
  suffix <- file_info[[cluster_name]]
  cluster_data <- cluster_data %>%
    mutate(Gene = paste0(Gene, "_", suffix))
  
  # Store the modified data frame in the list
  all_matrices[[cluster_name]] <- cluster_data
}

# Combine all data frames by binding rows
combined_df <- bind_rows(all_matrices)

# View the combined data frame
print(head(combined_df))

# Write the final combined data frame to a CSV file
write.csv(combined_df, "Combined_ZTs_allclusters_cyclic_0.05p_matrix.csv", row.names = FALSE)
```


```{r}
Combined_ZTs_DeSeq_normalized_counts_matrix <- read_csv("Combined_ZTs_DeSeq_normalized_counts_matrix.csv")
Combined_ZTs_allclusters_cyclic_0_05p_matrix <- read_csv("Combined_ZTs_allclusters_cyclic_0.05p_matrix.csv")
# Merge the data based on a common column (assuming the common column is 'Gene')
merged_df <- left_join(Combined_ZTs_allclusters_cyclic_0_05p_matrix, Combined_ZTs_DeSeq_normalized_counts_matrix, by = "Gene")

# Write the merged data frame to a CSV file
write_csv(merged_df, "Combined_ZTs_Deseq_normalized_counts_cyclic_0.05p_matrix_All_Samples.csv")
```

WGCNA 
Set up the environment

```{r}
require(readr)
require(tidyverse)
require(WGCNA)
require(DiPALM)
require(pheatmap)
```

```{r}
Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples <- read_csv("Combined_ZTs_Deseq_normalized_counts_cyclic_0.05p_matrix_All_Samples.csv")

colnames(Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples)
# Assuming the data frame is named Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples

# Get the gene names
genes <- Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples$Gene

# Calculate the average of A and B for each time point
Combined_ZTs_Avg <- data.frame(
  Gene = genes,
  ZT0 = rowMeans(Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples[, c("ZT0A", "ZT0B")], na.rm = TRUE),
  ZT4 = rowMeans(Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples[, c("ZT04A", "ZT04B")], na.rm = TRUE),
  ZT8 = rowMeans(Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples[, c("ZT08A", "ZT08B")], na.rm = TRUE),
  ZT12 = rowMeans(Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples[, c("ZT12A", "ZT12B")], na.rm = TRUE),
  ZT16 = rowMeans(Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples[, c("ZT16A", "ZT16B")], na.rm = TRUE),
  ZT20 = rowMeans(Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples[, c("ZT20A", "ZT20B")], na.rm = TRUE),
  ZT24 = rowMeans(Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_All_Samples[, c("ZT24A")], na.rm = TRUE)
)

# View the resulting data frame
head(Combined_ZTs_Avg)

# Write the merged data frame to a CSV file
write_csv(Combined_ZTs_Avg, "Combined_ZTs_Deseq_normalized_counts_cyclic_0.05p_matrix_Avg.csv")
Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_Avg <- read_csv("Combined_ZTs_Deseq_normalized_counts_cyclic_0.05p_matrix_Avg.csv")
```

WGCNA 

```{r}
DF = data.frame(Combined_ZTs_Deseq_normalized_counts_cyclic_0_05p_matrix_Avg)
rownames(DF) <- DF[,1]
DF = subset(DF, 
            select = c(2,3,4,5,6,7,8))

TCs_List <- lapply(colnames(DF), function(tp) {
  data.frame(GeneID = rownames(DF), Expression = DF[, tp])
})

# Rename list elements to match original column names
names(TCs_List) <- colnames(DF)

noTreat <- lapply(TCs_List, function(x) {
  rownames(x) <- rownames(x)
  return(x)
})

## Cluster samples
sampleTree= hclust(dist(t(DF)), method = "average")

plot(sampleTree, main = "Using hclust to detect outliers", sub="", xlab="", cex.lab = 1.5,cex.axis = 1.5, cex.main = 2)

# Can allow parallel processing for multiple cores
#allowWGCNAThreads(8)
# Choose a set of soft-thresholding powers
powers = c(c(1:10), seq(from = 12, to = 50, by = 2))
cex1 = 0.9

## Estimate parameters for the network
# rows correspond to samples and columns to genes
threshold = pickSoftThreshold(t(DF), powerVector = powers, verbose = 5)


## Plot to select parameters
pdf("ParamEstimates.pdf", width = 8, height = 8)
# Scale free topology fit
plot(threshold$fitIndices[,1],
     -sign(threshold$fitIndices[,3])*threshold$fitIndices[,2],
     xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
     main = paste("Scale independence"));
text(threshold$fitIndices[,1],
     -sign(threshold$fitIndices[,3])*threshold$fitIndices[,2],
     labels=powers,cex=cex1,col="red")
abline(h=0.90,col="red")

# Mean connectivity as a function of the soft-thresholding power 
plot(threshold$fitIndices[,1], threshold$fitIndices[,5],
     xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
     main = paste("Mean connectivity"))
text(threshold$fitIndices[,1], threshold$fitIndices[,5], labels=powers, cex=cex1,col="red")
dev.off()

## Construct the network
BlockModsAll <- blockwiseModules(datExpr = t(DF), power = 30, networkType = "signed", corType="bicor", TOMType="signed", maxBlockSize = 14927, mergeCutHeight=0.2, deepSplit=1, pamRespectsDendro = F, nThreads = 4, verbose=3)

# save to avoid re-running in the future
##### CHANGE FILE NAME BASED ON GENOTYPE #####
save(BlockModsAll, file = "BlockModsAll.RData")

## Plot the module dendrograms
# convert labels to colors
mergedColors = labels2colors(BlockModsAll$colors)
# Assuming BlockModsAll is your list and contains the "colors" element
unique_colors <- unique(BlockModsAll[["colors"]])

# Print the unique colors
print(unique_colors)
pdf("ModuleDendros.pdf", width = 8, height = 8)
plotDendroAndColors(BlockModsAll$dendrograms[[1]], mergedColors[BlockModsAll$blockGenes[[1]]],
                    "Module colors",
                    dendroLabels = FALSE, hang = 0.03, addGuide = TRUE, guideHang = 0.05, 
                    ##### CHANGE #####
                    main = "Module Relationships")
dev.off()

# identify how many modules were detected
MEs = (BlockModsAll[[3]])


MEs = rownames_to_column(MEs, var = "Zts")

MEs$Zts = gsub("ZT", "", MEs$Zts)

# lengthen to plot the patterns
MEs = pivot_longer(MEs, cols = !Zts, names_to = "Modules", values_to = "Expression")

pdf("ModuleEigengenes.pdf", width = 8, height = 8)
MEs %>%
  ggplot(aes(x = as.numeric(Zts), y = Expression)) +
  geom_line() +
  facet_wrap(~Modules) +
  xlab("Zt") +
  ylab("Time series response") +
  ggtitle("Co-expression Eigengene Patterns") +
  theme_bw()
dev.off()
```

```{r}
# Extract the colors vector from BlockModsAll
colors_vector <- BlockModsAll[["colors"]]

# Convert to data frame
moduleColors_df <- data.frame(GeneID = names(colors_vector), Color = colors_vector, row.names = NULL)

# Show the resulting data frame
print(moduleColors_df)
write.csv(moduleColors_df, file = "gene_modules.csv", row.names = FALSE)
# Assuming moduleColors_df is your data frame
colors <- unique(moduleColors_df$Color)

# Create a list to store subsets
color_data_list <- list()

# Loop through each color and create subsets
for (color in colors) {
  # Subset data for the current color
  color_data <- moduleColors_df[moduleColors_df$Color == color, ]
  
  # Store subset in list with color name as key
  color_data_list[[color]] <- color_data
  
  # Generate file name
  file_name <- paste0("module_", color, ".csv")
  
  # Write subset to CSV file
  write.csv(color_data, file = file_name, row.names = FALSE)
}

##### ##### ##### DIPALM ##### ##### #####
# Convert data frame to a list of matrices (each matrix for a time point)
# Convert data frame to a list with gene names as rows and expression values as columns
gene_list <- list(DF)

# Display the resulting list
print(gene_list)
# re-set MEs
MEs = (BlockModsAll[[3]])
# where kME is the pattern change difference, and Med is the difference in median expression
kMEsList<-BuildModMembership(MeMat = MEs, TCsLst = gene_list)

# Check the names of the elements
names(kMEsList)

# Loop through each element in the kMEsList
for (name in names(kMEsList)) {
  # Convert the list element to a data frame
  df <- as.data.frame(kMEsList[[name]])
  
  # Add row names as a new column 'CycID'
  df$CycID <- rownames(df)
  
  # Rename the score column to 'ModuleMembership_score'
  colnames(df)[1] <- "ModuleMembership_score"
  
  # Reorder columns to have CycID as the first column
  df <- df[, c("CycID", "ModuleMembership_score")]
  
  # Create a file name using the element name
  file_name <- paste0(name, ".csv")
  
  # Save the data frame as a CSV file
  write.csv(df, file_name, row.names = FALSE)
}

# Optionally, print a message indicating the files have been saved
print("CSV files have been saved.")
################################################
#Add JTK data to each module

setwd("~/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster/0.05p_sorted_JTK_Data")
library(readxl)
# List of file names
file_names <- c("Cluster0_0.05.xlsx", 
                "Cluster1_0.05.xlsx", 
                "Cluster2_0.05.xlsx", 
                "Cluster3_0.05.xlsx", 
                "Cluster4_0.05.xlsx", 
                "Cluster5_0.05.xlsx", 
                "Cluster6_0.05.xlsx", 
                "Cluster7_0.05.xlsx", 
                "Cluster8_0.05.xlsx", 
                "Cluster9_0.05.xlsx", 
                "Cluster10_0.05.xlsx", 
                "Cluster11_0.05.xlsx", 
                "Cluster12_0.05.xlsx", 
                "Cluster13_0.05.xlsx", 
                "Cluster14_0.05.xlsx", 
                "Cluster15_0.05.xlsx",
                "Cluster16_0.05.xlsx", 
                "Cluster17_0.05.xlsx", 
                "Cluster18_0.05.xlsx")


# Initialize an empty list to store the data frames
all_matrices <- list()

# Loop through each file name to read and store the data frames
for (file in file_names) {
  # Read the matrix data from the CSV file
  matrix_data <- read_xlsx(file)
  
  # Extract the cluster number from the file name
  cluster_number <- sub(".*Cluster([0-9]+).*", "\\1", file)
  
  # Add the cluster number to the gene IDs
  matrix_data <- matrix_data %>%
    mutate(CycID = paste0(CycID, "_", cluster_number))
  
  # Store the data frame in the list
  all_matrices <- append(all_matrices, list(matrix_data))
}


setwd("~/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster")
library(dplyr)

# Check column types (optional, for understanding the issue)
lapply(all_matrices, function(df) sapply(df, class))

# Convert ADJ.P column to numeric in all data frames
all_matrices <- lapply(all_matrices, function(df) {
  df$ADJ.P <- as.numeric(df$ADJ.P)
  df
})

# Combine the data frames
combined_df <- bind_rows(all_matrices)

# View the combined data frame
print(head(combined_df))

write.csv(combined_df, "JTK_ALL_Clusters_matrix_0.05p.csv", row.names = FALSE)

gene_modules <- read_csv("gene_modules.csv")
# Ensure it is a data frame
gene_modules <- as.data.frame(gene_modules)

colnames(gene_modules)

# Perform the join
merged_df <- left_join(combined_df, gene_modules, by = c("CycID" = "GeneID"))

write.csv(merged_df, "JTK_ALL_Clusters_Module_Colors_matrix_0.05p.csv", row.names = FALSE)

JTK_ALL_Clusters_matrix_0_05p <- read_csv("JTK_ALL_Clusters_matrix_0.05p.csv")


###########################
#Calculating zScore 

Expression_Normalised <- read_csv("Combined_ZTs_Deseq_normalized_counts_cyclic_0.05p_matrix_Avg.csv")

# Convert Expression_Normalised to a data frame if it's not already
Expression_Normalised <- as.data.frame(Expression_Normalised)
# Assuming Expression_Normalised is your data frame
colnames(Expression_Normalised)


colnames(merged_df)

# Perform the join
merged_df <- left_join(merged_df, Expression_Normalised, by = c("CycID" = "Gene"))

# Check the first few rows of the resulting data frame
head(merged_df)

write.csv(merged_df, "JTK_Clusters_Module_Colors_Expression_matrix_0.05.csv", row.names = FALSE)

colnames(merged_df)

JTK_Clusters_Module_Colors_Expression_matrix_0_05 <- read_csv("JTK_Clusters_Module_Colors_Expression_matrix_0.05.csv")

# Define the columns representing the expression values
expression_columns <- colnames(JTK_Clusters_Module_Colors_Expression_matrix_0_05)[grepl("^ZT", colnames(JTK_Clusters_Module_Colors_Expression_matrix_0_05))]

# Reshape the data to long format for easier manipulation
merged_data_long <- JTK_Clusters_Module_Colors_Expression_matrix_0_05 %>%
  pivot_longer(cols = all_of(expression_columns), names_to = "ZT", values_to = "Expression") %>%
  mutate(ReplicateGroup = sub("([A-Za-z0-9]+)[A-B]$", "\\1", ZT))



library(tidyr)

# Example assuming merged_data_long is your data frame
merged_data_long <- merged_data_long %>%
  separate(col = 'CycID', into = c("gid", "cluster"), sep = "_", remove = FALSE)

# Print the modified data frame
print(merged_data_long)
colnames(merged_data_long)
# Calculate the average and standard deviation of replicates at each ZT for each gene
merged_data_long <- merged_data_long %>%
  group_by(CycID, ReplicateGroup) %>%
  mutate(AvgExprs = mean(Expression, na.rm = TRUE),
         sdExprs = sd(Expression, na.rm = TRUE)) %>%
  ungroup()
library(dplyr)


subsetted_data <- merged_data_long %>%
  select(CycID, ADJ.P, PER, LAG, AMP, Color, ReplicateGroup, AvgExprs) %>%
  distinct(CycID, ReplicateGroup, .keep_all = TRUE)  # Keep only unique combinations of Gene and ZT

# Print the subsetted data
print(subsetted_data)

subsetted_data <- subsetted_data %>%
  separate(col = 'CycID', into = c("gid", "cluster"), sep = "_", remove = FALSE)# Calculate the average and standard deviation over the whole time course by gene
colnames(subsetted_data)

library(dplyr)
# Pivot the data to wide format
wide_data <- subsetted_data %>%
  pivot_wider(
    id_cols = CycID,  # Column containing gene identifiers
    names_from = ReplicateGroup,  # Column with time point identifiers (ZT0, ZT04, etc.)
    values_from = AvgExprs  # Values to populate the matrix
  )


# Print the wide format data
print(wide_data)

# Calculate average expression for each gene across all time points
wide_data$TCavg <- rowMeans(wide_data[, -1])  # Calculate row means excluding the CycID column

# Calculate standard deviation for each gene across all time points
wide_data$TCsd <- apply(wide_data[, -1], 1, sd)  # Calculate standard deviation across each row

# Print the results
print(wide_data[, c("CycID", "TCavg", "TCsd")])

colnames(wide_data)
# Create a new data frame with CycID, TCavg, and TCsd only
wide_data <- wide_data[, c("CycID", "TCavg", "TCsd")]
# Merge calculated metrics back into wide_data
subsetted_data <- subsetted_data %>%
  left_join(wide_data, by = "CycID")

# Calculate the z-score
subsetted_data <- subsetted_data %>%
  mutate(zScore = (AvgExprs - TCavg)/TCsd)

colnames(subsetted_data)

write.csv(subsetted_data, "zScore_Module_Colors_Expression_matrix_0_05.csv", row.names = FALSE)

cleaned_data = subsetted_data
# Ensure 'ReplicateGroup' is treated as a factor and ordered correctly
cleaned_data$ReplicateGroup <- factor(cleaned_data$ReplicateGroup, levels = unique(cleaned_data$ReplicateGroup))

# Generate the plot
p <- ggplot(cleaned_data, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(CycID, Color)), alpha = 0.5) +
  facet_wrap(~ Color, scales = "free_y", ncol = 3) +
  theme_minimal() +
  labs(title = "Z-Scores for Each Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))  # Adjusting the vertical and horizontal justification

# Print the plot to the interactive session
print(p)

# Save the plot to a PDF file with specified width and height
ggsave("plot_zscore_0.05p.pdf", plot = p, width = 20, height = 20)


# Get unique colors from cleaned_data
colors <- unique(cleaned_data$Color)

# Open a PDF device
pdf("ZScores_All_Colors_0.05p.pdf")

# Loop through each color
for (color in colors) {
  # Subset data for the current color
  color_data <- subset(cleaned_data, Color == color)
  
  # Ensure 'ReplicateGroup' is treated as a factor and ordered correctly within the subset
  color_data$ReplicateGroup <- factor(color_data$ReplicateGroup, levels = unique(color_data$ReplicateGroup))
  
  # Create the plot
  p <- ggplot(color_data, aes(x = ReplicateGroup, y = zScore)) +
    geom_line(aes(group = interaction(CycID, Color)), alpha = 0.5) +
    theme_minimal() +
    labs(title = paste("Z-Scores for Color:", color),
         x = "Time Points (ZT)",
         y = "Z-Score") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))  # Adjusting the vertical and horizontal justification
  
  # Print the plot to the PDF device
  print(p)
}

# Close the PDF device
dev.off()
```

#########Average zScore Plots for each module

Filtering Modules by Membership_score 0.6

```{r}
module_black <- read_csv("module_black.csv")
MEblack <- read_csv("MEblack.csv")

# Perform the join
merged_df <- left_join(module_black, MEblack, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEblack_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEblack_0_6 <- read_csv("MEblack_0.6.csv")
MEblack_0_6_df <- left_join(MEblack_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEblack_0_6_df, "zScore_MEblack_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEblack_0_6_df <- transform(MEblack_0_6_df, Color = Color.x)
MEblack_0_6_df$ReplicateGroup <- factor(MEblack_0_6_df$ReplicateGroup, levels = unique(MEblack_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEblack_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEblack_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEblack_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEblack_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEblack_0_6_df$ReplicateGroup <- as.factor(MEblack_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEblack_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEblack",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
p
ggsave(filename = "Average Z Score_MEblack.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_blue <- read_csv("module_blue.csv")
MEblue <- read_csv("MEblue.csv")

# Perform the join
merged_df <- left_join(module_blue, MEblue, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEblue_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEblue_0_6 <- read_csv("MEblue_0.6.csv")
MEblue_0_6_df <- left_join(MEblue_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEblue_0_6_df, "zScore_MEblue_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEblue_0_6_df <- transform(MEblue_0_6_df, Color = Color.x)
MEblue_0_6_df$ReplicateGroup <- factor(MEblue_0_6_df$ReplicateGroup, levels = unique(MEblue_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEblue_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEblue_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEblue_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEblue_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEblue_0_6_df$ReplicateGroup <- as.factor(MEblue_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEblue_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEblue",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEblue.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_brown <- read_csv("module_brown.csv")
MEbrown <- read_csv("MEbrown.csv")

# Perform the join
merged_df <- left_join(module_brown, MEbrown, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEbrown_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEbrown_0_6 <- read_csv("MEbrown_0.6.csv")
MEbrown_0_6_df <- left_join(MEbrown_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEbrown_0_6_df, "zScore_MEbrown_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEbrown_0_6_df <- transform(MEbrown_0_6_df, Color = Color.x)
MEbrown_0_6_df$ReplicateGroup <- factor(MEbrown_0_6_df$ReplicateGroup, levels = unique(MEbrown_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEbrown_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEbrown_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEbrown_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEbrown_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEbrown_0_6_df$ReplicateGroup <- as.factor(MEbrown_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEbrown_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEbrown",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEbrown.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_cyan <- read_csv("module_cyan.csv")
MEcyan <- read_csv("MEcyan.csv")

# Perform the join
merged_df <- left_join(module_cyan, MEcyan, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEcyan_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEcyan_0_6 <- read_csv("MEcyan_0.6.csv")
MEcyan_0_6_df <- left_join(MEcyan_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEcyan_0_6_df, "zScore_MEcyan_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEcyan_0_6_df <- transform(MEcyan_0_6_df, Color = Color.x)
MEcyan_0_6_df$ReplicateGroup <- factor(MEcyan_0_6_df$ReplicateGroup, levels = unique(MEcyan_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEcyan_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEcyan_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEcyan_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEcyan_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEcyan_0_6_df$ReplicateGroup <- as.factor(MEcyan_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEcyan_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEcyan",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEcyan.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_darkgreen <- read_csv("module_darkgreen.csv")
MEdarkgreen <- read_csv("MEdarkgreen.csv")

# Perform the join
merged_df <- left_join(module_darkgreen, MEdarkgreen, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEdarkgreen_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEdarkgreen_0_6 <- read_csv("MEdarkgreen_0.6.csv")
MEdarkgreen_0_6_df <- left_join(MEdarkgreen_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEdarkgreen_0_6_df, "zScore_MEdarkgreen_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEdarkgreen_0_6_df <- transform(MEdarkgreen_0_6_df, Color = Color.x)
MEdarkgreen_0_6_df$ReplicateGroup <- factor(MEdarkgreen_0_6_df$ReplicateGroup, levels = unique(MEdarkgreen_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEdarkgreen_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEdarkgreen_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEdarkgreen_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEdarkgreen_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEdarkgreen_0_6_df$ReplicateGroup <- as.factor(MEdarkgreen_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEdarkgreen_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEdarkgreen",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEdarkgreen.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_darkgrey <- read_csv("module_darkgrey.csv")
MEdarkgrey <- read_csv("MEdarkgrey.csv")

# Perform the join
merged_df <- left_join(module_darkgrey, MEdarkgrey, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEdarkgrey_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEdarkgrey_0_6 <- read_csv("MEdarkgrey_0.6.csv")
MEdarkgrey_0_6_df <- left_join(MEdarkgrey_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEdarkgrey_0_6_df, "zScore_MEdarkgrey_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEdarkgrey_0_6_df <- transform(MEdarkgrey_0_6_df, Color = Color.x)
MEdarkgrey_0_6_df$ReplicateGroup <- factor(MEdarkgrey_0_6_df$ReplicateGroup, levels = unique(MEdarkgrey_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEdarkgrey_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEdarkgrey_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEdarkgrey_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEdarkgrey_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEdarkgrey_0_6_df$ReplicateGroup <- as.factor(MEdarkgrey_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEdarkgrey_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEdarkgrey",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEdarkgrey.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_darkturquoise <- read_csv("module_darkturquoise.csv")
MEdarkturquoise <- read_csv("MEdarkturquoise.csv")

# Perform the join
merged_df <- left_join(module_darkturquoise, MEdarkturquoise, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEdarkturquoise_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEdarkturquoise_0_6 <- read_csv("MEdarkturquoise_0.6.csv")
MEdarkturquoise_0_6_df <- left_join(MEdarkturquoise_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEdarkturquoise_0_6_df, "zScore_MEdarkturquoise_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEdarkturquoise_0_6_df <- transform(MEdarkturquoise_0_6_df, Color = Color.x)
MEdarkturquoise_0_6_df$ReplicateGroup <- factor(MEdarkturquoise_0_6_df$ReplicateGroup, levels = unique(MEdarkturquoise_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEdarkturquoise_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEdarkturquoise_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEdarkturquoise_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEdarkturquoise_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEdarkturquoise_0_6_df$ReplicateGroup <- as.factor(MEdarkturquoise_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEdarkturquoise_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEdarkturquoise",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEdarkturquoise.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_green <- read_csv("module_green.csv")
MEgreen <- read_csv("MEgreen.csv")

# Perform the join
merged_df <- left_join(module_green, MEgreen, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEgreen_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEgreen_0_6 <- read_csv("MEgreen_0.6.csv")
MEgreen_0_6_df <- left_join(MEgreen_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEgreen_0_6_df, "zScore_MEgreen_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEgreen_0_6_df <- transform(MEgreen_0_6_df, Color = Color.x)
MEgreen_0_6_df$ReplicateGroup <- factor(MEgreen_0_6_df$ReplicateGroup, levels = unique(MEgreen_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEgreen_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEgreen_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEgreen_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEgreen_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEgreen_0_6_df$ReplicateGroup <- as.factor(MEgreen_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEgreen_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEgreen",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEgreen.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_grey60 <- read_csv("module_grey60.csv")
MEgrey60 <- read_csv("MEgrey60.csv")

# Perform the join
merged_df <- left_join(module_grey60, MEgrey60, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEgrey60_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEgrey60_0_6 <- read_csv("MEgrey60_0.6.csv")
MEgrey60_0_6_df <- left_join(MEgrey60_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEgrey60_0_6_df, "zScore_MEgrey60_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEgrey60_0_6_df <- transform(MEgrey60_0_6_df, Color = Color.x)
MEgrey60_0_6_df$ReplicateGroup <- factor(MEgrey60_0_6_df$ReplicateGroup, levels = unique(MEgrey60_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEgrey60_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEgrey60_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEgrey60_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEgrey60_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEgrey60_0_6_df$ReplicateGroup <- as.factor(MEgrey60_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEgrey60_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEgrey60",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEgrey60.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_lightcyan <- read_csv("module_lightcyan.csv")
MElightcyan <- read_csv("MElightcyan.csv")

# Perform the join
merged_df <- left_join(module_lightcyan, MElightcyan, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MElightcyan_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MElightcyan_0_6 <- read_csv("MElightcyan_0.6.csv")
MElightcyan_0_6_df <- left_join(MElightcyan_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MElightcyan_0_6_df, "zScore_MElightcyan_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MElightcyan_0_6_df <- transform(MElightcyan_0_6_df, Color = Color.x)
MElightcyan_0_6_df$ReplicateGroup <- factor(MElightcyan_0_6_df$ReplicateGroup, levels = unique(MElightcyan_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MElightcyan_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MElightcyan_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MElightcyan_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MElightcyan_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MElightcyan_0_6_df$ReplicateGroup <- as.factor(MElightcyan_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MElightcyan_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MElightcyan",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MElightcyan.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_lightgreen <- read_csv("module_lightgreen.csv")
MElightgreen <- read_csv("MElightgreen.csv")

# Perform the join
merged_df <- left_join(module_lightgreen, MElightgreen, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MElightgreen_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MElightgreen_0_6 <- read_csv("MElightgreen_0.6.csv")
MElightgreen_0_6_df <- left_join(MElightgreen_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MElightgreen_0_6_df, "zScore_MElightgreen_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MElightgreen_0_6_df <- transform(MElightgreen_0_6_df, Color = Color.x)
MElightgreen_0_6_df$ReplicateGroup <- factor(MElightgreen_0_6_df$ReplicateGroup, levels = unique(MElightgreen_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MElightgreen_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MElightgreen_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MElightgreen_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MElightgreen_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MElightgreen_0_6_df$ReplicateGroup <- as.factor(MElightgreen_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MElightgreen_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MElightgreen",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MElightgreen.pdf", plot = p)
dev.off()
#Filtering Modules by Membership_score 0.6
module_lightyellow <- read_csv("module_lightyellow.csv")
MElightyellow <- read_csv("MElightyellow.csv")

# Perform the join
merged_df <- left_join(module_lightyellow, MElightyellow, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MElightyellow_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MElightyellow_0_6 <- read_csv("MElightyellow_0.6.csv")
MElightyellow_0_6_df <- left_join(MElightyellow_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MElightyellow_0_6_df, "zScore_MElightyellow_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MElightyellow_0_6_df <- transform(MElightyellow_0_6_df, Color = Color.x)
MElightyellow_0_6_df$ReplicateGroup <- factor(MElightyellow_0_6_df$ReplicateGroup, levels = unique(MElightyellow_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MElightyellow_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MElightyellow_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MElightyellow_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MElightyellow_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MElightyellow_0_6_df$ReplicateGroup <- as.factor(MElightyellow_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MElightyellow_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MElightyellow",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MElightyellow.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_magenta <- read_csv("module_magenta.csv")
MEmagenta <- read_csv("MEmagenta.csv")

# Perform the join
merged_df <- left_join(module_magenta, MEmagenta, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEmagenta_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEmagenta_0_6 <- read_csv("MEmagenta_0.6.csv")
MEmagenta_0_6_df <- left_join(MEmagenta_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEmagenta_0_6_df, "zScore_MEmagenta_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEmagenta_0_6_df <- transform(MEmagenta_0_6_df, Color = Color.x)
MEmagenta_0_6_df$ReplicateGroup <- factor(MEmagenta_0_6_df$ReplicateGroup, levels = unique(MEmagenta_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEmagenta_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEmagenta_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEmagenta_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEmagenta_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEmagenta_0_6_df$ReplicateGroup <- as.factor(MEmagenta_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEmagenta_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEmagenta",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEmagenta.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_midnightblue <- read_csv("module_midnightblue.csv")
MEmidnightblue <- read_csv("MEmidnightblue.csv")

# Perform the join
merged_df <- left_join(module_midnightblue, MEmidnightblue, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEmidnightblue_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEmidnightblue_0_6 <- read_csv("MEmidnightblue_0.6.csv")
MEmidnightblue_0_6_df <- left_join(MEmidnightblue_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEmidnightblue_0_6_df, "zScore_MEmidnightblue_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEmidnightblue_0_6_df <- transform(MEmidnightblue_0_6_df, Color = Color.x)
MEmidnightblue_0_6_df$ReplicateGroup <- factor(MEmidnightblue_0_6_df$ReplicateGroup, levels = unique(MEmidnightblue_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEmidnightblue_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEmidnightblue_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEmidnightblue_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEmidnightblue_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEmidnightblue_0_6_df$ReplicateGroup <- as.factor(MEmidnightblue_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEmidnightblue_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEmidnightblue",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEmidnightblue.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_pink <- read_csv("module_pink.csv")
MEpink <- read_csv("MEpink.csv")

# Perform the join
merged_df <- left_join(module_pink, MEpink, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEpink_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEpink_0_6 <- read_csv("MEpink_0.6.csv")
MEpink_0_6_df <- left_join(MEpink_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEpink_0_6_df, "zScore_MEpink_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEpink_0_6_df <- transform(MEpink_0_6_df, Color = Color.x)
MEpink_0_6_df$ReplicateGroup <- factor(MEpink_0_6_df$ReplicateGroup, levels = unique(MEpink_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEpink_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEpink_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEpink_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEpink_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEpink_0_6_df$ReplicateGroup <- as.factor(MEpink_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEpink_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEpink",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEpink.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_purple <- read_csv("module_purple.csv")
MEpurple <- read_csv("MEpurple.csv")

# Perform the join
merged_df <- left_join(module_purple, MEpurple, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEpurple_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEpurple_0_6 <- read_csv("MEpurple_0.6.csv")
MEpurple_0_6_df <- left_join(MEpurple_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEpurple_0_6_df, "zScore_MEpurple_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEpurple_0_6_df <- transform(MEpurple_0_6_df, Color = Color.x)
MEpurple_0_6_df$ReplicateGroup <- factor(MEpurple_0_6_df$ReplicateGroup, levels = unique(MEpurple_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEpurple_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEpurple_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEpurple_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEpurple_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEpurple_0_6_df$ReplicateGroup <- as.factor(MEpurple_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEpurple_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEpurple",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEpurple.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_red <- read_csv("module_red.csv")
MEred <- read_csv("MEred.csv")

# Perform the join
merged_df <- left_join(module_red, MEred, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEred_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEred_0_6 <- read_csv("MEred_0.6.csv")
MEred_0_6_df <- left_join(MEred_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEred_0_6_df, "zScore_MEred_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEred_0_6_df <- transform(MEred_0_6_df, Color = Color.x)
MEred_0_6_df$ReplicateGroup <- factor(MEred_0_6_df$ReplicateGroup, levels = unique(MEred_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEred_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEred_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEred_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEred_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEred_0_6_df$ReplicateGroup <- as.factor(MEred_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEred_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEred",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEred.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_royalblue <- read_csv("module_royalblue.csv")
MEroyalblue <- read_csv("MEroyalblue.csv")

# Perform the join
merged_df <- left_join(module_royalblue, MEroyalblue, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEroyalblue_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEroyalblue_0_6 <- read_csv("MEroyalblue_0.6.csv")
MEroyalblue_0_6_df <- left_join(MEroyalblue_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEroyalblue_0_6_df, "zScore_MEroyalblue_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEroyalblue_0_6_df <- transform(MEroyalblue_0_6_df, Color = Color.x)
MEroyalblue_0_6_df$ReplicateGroup <- factor(MEroyalblue_0_6_df$ReplicateGroup, levels = unique(MEroyalblue_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEroyalblue_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEroyalblue_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEroyalblue_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEroyalblue_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEroyalblue_0_6_df$ReplicateGroup <- as.factor(MEroyalblue_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEroyalblue_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEroyalblue",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEroyalblue.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_salmon <- read_csv("module_salmon.csv")
MEsalmon <- read_csv("MEsalmon.csv")

# Perform the join
merged_df <- left_join(module_salmon, MEsalmon, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEsalmon_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEsalmon_0_6 <- read_csv("MEsalmon_0.6.csv")
MEsalmon_0_6_df <- left_join(MEsalmon_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEsalmon_0_6_df, "zScore_MEsalmon_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEsalmon_0_6_df <- transform(MEsalmon_0_6_df, Color = Color.x)
MEsalmon_0_6_df$ReplicateGroup <- factor(MEsalmon_0_6_df$ReplicateGroup, levels = unique(MEsalmon_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEsalmon_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEsalmon_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEsalmon_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEsalmon_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEsalmon_0_6_df$ReplicateGroup <- as.factor(MEsalmon_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEsalmon_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEsalmon",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEsalmon.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_tan <- read_csv("module_tan.csv")
MEtan <- read_csv("MEtan.csv")

# Perform the join
merged_df <- left_join(module_tan, MEtan, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEtan_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEtan_0_6 <- read_csv("MEtan_0.6.csv")
MEtan_0_6_df <- left_join(MEtan_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEtan_0_6_df, "zScore_MEtan_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEtan_0_6_df <- transform(MEtan_0_6_df, Color = Color.x)
MEtan_0_6_df$ReplicateGroup <- factor(MEtan_0_6_df$ReplicateGroup, levels = unique(MEtan_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEtan_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEtan_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEtan_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEtan_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEtan_0_6_df$ReplicateGroup <- as.factor(MEtan_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEtan_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEtan",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEtan.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_turquoise <- read_csv("module_turquoise.csv")
MEturquoise <- read_csv("MEturquoise.csv")

# Perform the join
merged_df <- left_join(module_turquoise, MEturquoise, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEturquoise_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEturquoise_0_6 <- read_csv("MEturquoise_0.6.csv")
MEturquoise_0_6_df <- left_join(MEturquoise_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEturquoise_0_6_df, "zScore_MEturquoise_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEturquoise_0_6_df <- transform(MEturquoise_0_6_df, Color = Color.x)
MEturquoise_0_6_df$ReplicateGroup <- factor(MEturquoise_0_6_df$ReplicateGroup, levels = unique(MEturquoise_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEturquoise_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEturquoise_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEturquoise_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEturquoise_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEturquoise_0_6_df$ReplicateGroup <- as.factor(MEturquoise_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEturquoise_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEturquoise",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEturquoise.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_yellow <- read_csv("module_yellow.csv")
MEyellow <- read_csv("MEyellow.csv")

# Perform the join
merged_df <- left_join(module_yellow, MEyellow, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEyellow_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEyellow_0_6 <- read_csv("MEyellow_0.6.csv")
MEyellow_0_6_df <- left_join(MEyellow_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEyellow_0_6_df, "zScore_MEyellow_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEyellow_0_6_df <- transform(MEyellow_0_6_df, Color = Color.x)
MEyellow_0_6_df$ReplicateGroup <- factor(MEyellow_0_6_df$ReplicateGroup, levels = unique(MEyellow_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEyellow_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEyellow_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEyellow_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEyellow_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEyellow_0_6_df$ReplicateGroup <- as.factor(MEyellow_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEyellow_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEyellow",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEyellow.pdf", plot = p)
dev.off()
#Filtering Modules by Membership_score 0.6
module_darkorange <- read_csv("module_darkorange.csv")
MEdarkorange <- read_csv("MEdarkorange.csv")

# Perform the join
merged_df <- left_join(module_darkorange, MEdarkorange, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEdarkorange_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEdarkorange_0_6 <- read_csv("MEdarkorange_0.6.csv")
MEdarkorange_0_6_df <- left_join(MEdarkorange_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEdarkorange_0_6_df, "zScore_MEdarkorange_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEdarkorange_0_6_df <- transform(MEdarkorange_0_6_df, Color = Color.x)
MEdarkorange_0_6_df$ReplicateGroup <- factor(MEdarkorange_0_6_df$ReplicateGroup, levels = unique(MEdarkorange_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEdarkorange_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEdarkorange_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEdarkorange_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEdarkorange_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEdarkorange_0_6_df$ReplicateGroup <- as.factor(MEdarkorange_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEdarkorange_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEdarkorange",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEdarkorange.pdf", plot = p)
dev.off()


#Filtering Modules by Membership_score 0.6
module_orange <- read_csv("module_orange.csv")
MEorange <- read_csv("MEorange.csv")

# Perform the join
merged_df <- left_join(module_orange, MEorange, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEorange_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEorange_0_6 <- read_csv("MEorange_0.6.csv")
MEorange_0_6_df <- left_join(MEorange_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEorange_0_6_df, "zScore_MEorange_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEorange_0_6_df <- transform(MEorange_0_6_df, Color = Color.x)
MEorange_0_6_df$ReplicateGroup <- factor(MEorange_0_6_df$ReplicateGroup, levels = unique(MEorange_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEorange_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEorange_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEorange_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEorange_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEorange_0_6_df$ReplicateGroup <- as.factor(MEorange_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEorange_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEorange",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEorange.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_greenyellow <- read_csv("module_greenyellow.csv")
MEgreenyellow <- read_csv("MEgreenyellow.csv")

# Perform the join
merged_df <- left_join(module_greenyellow, MEgreenyellow, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEgreenyellow_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEgreenyellow_0_6 <- read_csv("MEgreenyellow_0.6.csv")
MEgreenyellow_0_6_df <- left_join(MEgreenyellow_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEgreenyellow_0_6_df, "zScore_MEgreenyellow_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEgreenyellow_0_6_df <- transform(MEgreenyellow_0_6_df, Color = Color.x)
MEgreenyellow_0_6_df$ReplicateGroup <- factor(MEgreenyellow_0_6_df$ReplicateGroup, levels = unique(MEgreenyellow_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEgreenyellow_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEgreenyellow_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEgreenyellow_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEgreenyellow_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEgreenyellow_0_6_df$ReplicateGroup <- as.factor(MEgreenyellow_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEgreenyellow_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEgreenyellow",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEgreenyellow.pdf", plot = p)
dev.off()

#Filtering Modules by Membership_score 0.6
module_darkred <- read_csv("module_darkred.csv")
MEdarkred <- read_csv("MEdarkred.csv")

# Perform the join
merged_df <- left_join(module_darkred, MEdarkred, by = c("GeneID" = "CycID"))

colnames(merged_df)

# Assuming merged_df is your data frame
filtered_df <- merged_df[merged_df$ModuleMembership_score > 0.6, c("GeneID", "Color", "ModuleMembership_score")]

# Print or further process filtered_df
print(filtered_df)

write.csv(filtered_df, file = "MEdarkred_0.6.csv", row.names = FALSE)

zScore_Module_Colors_Expression_matrix_0_05 <- read_csv("zScore_Module_Colors_Expression_matrix_0_05.csv")
MEdarkred_0_6 <- read_csv("MEdarkred_0.6.csv")
MEdarkred_0_6_df <- left_join(MEdarkred_0_6, zScore_Module_Colors_Expression_matrix_0_05, by = c("GeneID" = "CycID"))
write.csv(MEdarkred_0_6_df, "zScore_MEdarkred_0_6_df_0.05.csv", row.names = FALSE)

# Rename Color.x to Color
MEdarkred_0_6_df <- transform(MEdarkred_0_6_df, Color = Color.x)
MEdarkred_0_6_df$ReplicateGroup <- factor(MEdarkred_0_6_df$ReplicateGroup, levels = unique(MEdarkred_0_6_df$ReplicateGroup))

# Create the plot
plot <- ggplot(MEdarkred_0_6_df, aes(x = ReplicateGroup, y = zScore)) +
  geom_line(aes(group = interaction(GeneID, Color)), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Z-Scores for Color",
       x = "Time Points (ZT)",
       y = "Z-Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
# Print the plot to check for errors
print(plot)
# Save the plot as a PDF
ggsave(filename = "MEdarkred_ZScores_0.6MM_scor_0.05p.pdf", plot = plot)

colnames(MEdarkred_0_6_df)
###########
library(ggplot2)
library(dplyr)
library(ggplot2)
library(dplyr)
# Example data structure
# df <- data.frame(GeneID = rep(c("Gene1", "Gene2", "Gene3"), each = 5),
#                  ReplicateGroup = rep(1:5, times = 3),
#                  Zscore = rnorm(15))
# Check the structure of the data frame
str(MEdarkred_0_6_df)
# Ensure ReplicateGroup is treated as a factor or numeric
MEdarkred_0_6_df$ReplicateGroup <- as.factor(MEdarkred_0_6_df$ReplicateGroup)
# Calculate mean and standard deviation for each replicate group
df_summary <- MEdarkred_0_6_df %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )
# Create the line graph with shaded ribbon
p<- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), alpha = 0.2) +
  labs(title = "Average Z Score_MEdarkred",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal()
ggsave(filename = "Average Z Score_MEdarkred.pdf", plot = p)
dev.off()


```

```{r}
library(magick)
library(gridExtra)
library(ggplot2)
library(grid)
install.packages("pdftools")
install.packages("magick")
library(pdftools)
library(magick)
# Directory containing the PDF files
pdf_dir <- "/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster"
pdf_files <- list.files(pdf_dir, pattern = "Average Z Score_.*\\.pdf$", full.names = TRUE)

# Function to convert a PDF to a raster image (PNG format)
pdf_to_image <- function(pdf_file) {
  image_read_pdf(pdf_file, density = 150) # Increase density for better resolution
}

# Convert all PDFs to images
images <- lapply(pdf_files, pdf_to_image)

# Combine images into a single figure using gridExtra
image_plots <- lapply(images, function(img) {
  rasterGrob(as.raster(img), interpolate = TRUE)
})

# Define layout for combining plots
combined_plot <- marrangeGrob(grobs = image_plots, nrow = 10, ncol = 3)

# Save the combined plot to a single PDF
pdf("Combined_Modules_Average_ZScores_All2.pdf", width = 20, height = 15)
grid.draw(combined_plot)
dev.off()


# Define layout for combining plots (6 rows and 5 columns for 26 graphs)
combined_plot <- marrangeGrob(grobs = image_plots, nrow = 6, ncol = 5)

# Save the combined plot to a single PDF
pdf("Combined_Modules_Average_ZScores_All3.pdf", width = 20, height = 15)
grid.draw(combined_plot)
dev.off()

##################
#making one big data frame for all

# Load necessary libraries
library(dplyr)

# Define the directory containing your CSV files
csv_dir <- "/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster"  # Change this to your actual directory

# List all CSV files in the directory (assuming all are relevant)
csv_files <- list.files(csv_dir, pattern = "_0.6.csv$", full.names = TRUE)

# Read each CSV file and store them in a list of data frames
data_list <- lapply(csv_files, read.csv)

# Optionally: Ensure all data frames have the same structure (column names and order)
# Example: If you want to merge them by columns, ensure the column names match
# You can check column names for each file using colnames(data_list[[1]])

# Combine all data frames into one big matrix (by rows or columns)
# To combine by columns (add columns from each CSV):
combined_matrix <- bind_cols(data_list)

# If you want to merge by rows (add rows from each CSV):
# combined_matrix <- bind_rows(data_list)

# Optionally: Add a new column to identify the source file for each module
# This can help if you want to trace which data came from which module
for (i in seq_along(data_list)) {
  data_list[[i]]$Module <- gsub("_0.6.csv", "", basename(csv_files[i]))  # Extract module name
}

# Combine by rows to keep all data (adding a 'Module' column to trace the source)
combined_matrix <- bind_rows(data_list)

# Save the combined matrix to a new CSV file
write.csv(combined_matrix, "combined_matrix_all_modules.csv", row.names = FALSE)

# Print the first few rows of the combined matrix to check
head(combined_matrix)

# Assuming 'combined_matrix' is the data frame that contains your data

# Extract gene names (e.g., "AT1G01520" from "AT1G01520_0") from the 'GeneID' column
combined_matrix$GeneName <- gsub("_.*", "", combined_matrix$GeneID)

# Check the result
head(combined_matrix)

# Save the combined matrix to a new CSV file
write.csv(combined_matrix, "combined_matrix_all_modules.csv", row.names = FALSE)



# Remove duplicates by GeneName and Module, keeping only unique combinations
unique_genes <- combined_matrix %>%
  distinct(GeneName, Module, .keep_all = TRUE)

# View the resulting data frame
print(unique_genes)



# Count the number of distinct modules each gene appears in
gene_module_count <- combined_matrix %>%
  group_by(GeneName) %>%
  summarise(num_modules = n_distinct(Module)) %>%
  filter(num_modules > 1)

# Now filter the original data frame to include only genes that appear in multiple modules
genes_in_multiple_modules <- combined_matrix %>%
  filter(combined_matrix$GeneName %in% gene_module_count$GeneName)

# View the resulting data frame
print(genes_in_multiple_modules)


write.csv(genes_in_multiple_modules, "genes_in_multiple_modules.csv", row.names = FALSE)

```

Hierarchical clustering of the modules
Corelation matrix and heatmap
```{r}
library(dplyr)
library(tidyr)
library(pheatmap)
"/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster"
# Step 1: Define the list of module files
module_files <- list.files(pattern = "zScore_ME.*_0.6_df_0.05.csv") # Matches files like MEdarkred_0.6.csv, etc.

# Step 2: Read and process each file
module_expression_list <- list()

for (file in module_files) {
  # Read the file
  module_data <- read_csv(file)
  
  # Extract the module name from the filename
  module_name <- gsub("ME|_0.6.csv", "", file)
  
  # Calculate the mean z-score for each replicate group
  module_expression <- module_data %>%
    group_by(ReplicateGroup) %>%
    summarise(mean_zScore = mean(zScore, na.rm = TRUE), .groups = "drop") %>%
    mutate(Module = module_name)
  
  # Add the result to the list
  module_expression_list[[module_name]] <- module_expression
}

# Step 3: Combine all modules into a single data frame
combined_expression <- bind_rows(module_expression_list)
library(tibble)
# Step 4: Reshape data into a wide format (modules as columns, replicate groups as rows)
module_matrix <- combined_expression %>%
  pivot_wider(names_from = Module, values_from = mean_zScore) %>%
  column_to_rownames("ReplicateGroup")

# Step 5: Calculate the correlation matrix
correlation_matrix <- cor(module_matrix, use = "pairwise.complete.obs")

# Assuming `correlation_matrix` is your correlation matrix
# Get the current row and column names
current_names <- rownames(correlation_matrix)

# Replace the names using gsub
updated_names <- gsub("zScore_|_0_6_df_0.05|\\.csv", "", current_names)
updated_names <- paste0("ME", updated_names)

# Assign the updated names back to the matrix
rownames(correlation_matrix) <- updated_names
colnames(correlation_matrix) <- updated_names

colnames(correlation_matrix)

library(viridis)
# Step 6: Plot the correlation heatmap
heatmapColors <- viridis(50, option = "inferno")

pheatmap(
  correlation_matrix,
  cluster_rows = TRUE,    # Cluster modules
  cluster_cols = TRUE,    # Cluster modules
  color = heatmapColors, # Color gradient
  main = "Module Correlation Heatmap"
)

# Save the heatmap as a PDF
pdf("Module_Correlation_Heatmap_0.6.pdf")
pheatmap(
  correlation_matrix,
  cluster_rows = TRUE,
  cluster_cols = TRUE,
  color = colorRampPalette(c("blue", "white", "red"))(50),
  main = "Module Correlation Heatmap"
)
dev.off()

# Hierarchical clustering

sampleTree <- hclust(dist(t(correlation_matrix)), method = "average")

plot(sampleTree)

# 1. Calculate the distance matrix and perform hierarchical clustering (as you're already doing)
distance_matrix <- dist(t(correlation_matrix))
hc <- hclust(distance_matrix, method = "average")

# 2. Create a vector of numbers to use as labels
num_labels <- 1:length(hc$labels) # Generates numbers from 1 to the number of modules

# 3. Plot the dendrogram with the new labels
plot(hc, labels = num_labels,
     main = "Cluster Dendrogram",
     xlab = NULL, ylab = "Height")
```

Module_data_sorted_on_basis_of_Hierarichal_clusterin_0.6mm

```{r}
setwd("~/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster")

####Code to make big data frame after hierarichal slustering of filtered modules on basis of average zScore for each replicate group

library(tidyverse)

# Directory containing module files
module_dir <- "/Users/alveenazulfiqar/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster"

# List all files matching the pattern
module_files <- list.files(module_dir, pattern = "zScore_ME.*_0.6_df_0.05.csv", full.names = TRUE)

# Initialize an empty list to store data
all_clade_data <- list()

# Define clade assignments (based on dendrogram)
clade_map <- list(
  Clade1 = c("MEpink", "MEpurple", "MEdarkred", "MEdarkgreen", "MEtan"),
  Clade2 = c("MEmagenta", "MEgreen", "MEroyalblue", "MEorange", "MElightcyan", "MEblue", "MElightyellow"),
  Clade3 = c("MEdarkorange", "MEsalmon", "MEbrown", "MEdarkgrey"),
  Clade4 = c("MEcyan", "MEgreenyellow", "MEyellow", "MEdarkturquoise", "MEred"),
  Clade5 = c("MEblack", "MEgrey60", "MEturquoise", "MElightgreen", "MEmidnightblue")
)


head(clade_map)


# Flatten the clade_map
clade_map_flat <- stack(clade_map)
colnames(clade_map_flat) <- c("Module", "Clade")


# Process each file
for (file in module_files) {
  # Read the file
  module_data <- read_csv(file)
  
  # Extract the module name from the filename
  module_name <- str_extract(file, "ME[a-zA-Z0-9]+")
  
  # Add the module and clade info to the data
  module_data <- module_data %>%
    mutate(
      Module = module_name,
      Clade = clade_map_flat$Clade[match(module_name, clade_map_flat$Module)]
    )
  
  # Append to the list
  all_clade_data[[module_name]] <- module_data
}

# Combine all data into a single data frame
final_clade_df <- bind_rows(all_clade_data)

###Subsetting data frame to have Gene info followed by cluster info and clade info

library(tidyverse)
library(dplyr)
# Assuming the input data frame is named 'df'
# Example: Read the input file
# df <- read_csv("your_file.csv")

# Extract the TAIR Gene ID and Cluster
final_clade_df <- final_clade_df %>%
  mutate(
    Gene = sub("_.*", "", GeneID),     # Extract TAIR Gene ID
    Cluster = sub(".*_", "", GeneID)  # Extract Cluster number
  )

final_clade_df <- as_tibble(final_clade_df)

subset_df2 <- final_clade_df %>%
  dplyr::select(Gene, Cluster, Clade, Module) %>%
  distinct(Gene, Module, Cluster, .keep_all = TRUE)


# Step 1: Add "Cluster" as a column with the prefix "Cluster"
df <- subset_df2 %>%
  mutate(Cluster = paste0("Cluster", Cluster))  # Add prefix "Cluster" to the cluster numbers
library(tidyr)

df <- as.data.frame(df)

names(df)
library(dplyr)
library(tidyr)

reshaped_df1 <- df %>%
  dplyr::select(Gene, Cluster, Clade) %>%   # Explicitly call select from dplyr
  pivot_wider(
    names_from = Cluster,                  # Use "Cluster" column to create new columns
    values_from = Cluster,                 # Populate values with the Cluster info
    values_fill = list(Cluster = NA)       # Fill missing values with NA
  )

X <- apply(reshaped_df1, 1, function(row) {
  # Identify which columns (from 3 onward) are NOT NA
  non_na_indices <- which(!is.na(row[3:length(row)])) 
  
  # Create a result vector with NA, preserving the first element
  result <- row
  result[3:length(row)] <- NA  # Set all columns from 3 onward to NA
  
  # Replace the non-NA positions with the Clade value (second column)
  result[non_na_indices + 2] <- row[2]
  
  return(result)
})


# Transpose the result
X_transposed <- t(X)

# Convert the transposed result to a data frame
df_result <- as.data.frame(X_transposed, stringsAsFactors = FALSE)

# Optional: Rename the columns based on the original structure, if necessary
colnames(df_result) <- colnames(reshaped_df1)

# View the final data frame
df_result


df_result <- df_result[, !colnames(df_result) %in% "Clade"]

library(dplyr)

# Consolidate rows for the same Gene
df_result_consolidated <- df_result %>%
  group_by(Gene) %>%                              # Group by the Gene column
  summarize(across(everything(), ~ 
                     ifelse(all(is.na(.)), NA, paste(na.omit(.), collapse = ",")), .names = "consolidated_{col}")) %>% ungroup()                           # For each column, combine non-NA values
df_result_consolidated

colnames(df_result_consolidated) <- colnames(df_result)


# Optional: Save the reshaped data to a CSV file
write_csv(df_result_consolidated, "Gene_Clade_consolidated_0.6MM_frame.csv")



# Install if needed
install.packages("BiocManager")
BiocManager::install("org.At.tair.db")

# Load the package
library(org.At.tair.db)
columns(org.At.tair.db)
# Extract TAIR IDs for each Gene
gene_tair_ids <- select(org.At.tair.db, keys = df_result_consolidated$Gene, columns = "GENENAME", keytype = "TAIR")




colnames(df_result_consolidated)
colnames(gene_tair_ids)


merged_df <- merge(df_result_consolidated, gene_tair_ids, by.x = "Gene", by.y = "TAIR")

# Step 4: Sort the data frame by ClusterCount in descending order
merged_df <- merged_df %>%
  arrange(desc(ClusterCount)) 

# Optional: Save the reshaped data to a CSV file
write_csv(merged_df, "Gene_Clade_consolidated_annotated_module_0.6MM_frame.csv")
```

Average Clade Graphs(Figure 3 A)

```{r}
setwd("~/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster")

library(ggplot2)
library(readr)
library(dplyr)
library(magrittr)

#clade1

zScore_MEtan_0_6_df_0_05 <- read_csv("zScore_MEtan_0_6_df_0.05.csv")

MEtan_0_6_df <- transform(zScore_MEtan_0_6_df_0_05, Color = Color.x)


zScore_MEpink_0_6_df_0_05 <- read_csv("zScore_MEpink_0_6_df_0.05.csv")

MEpink_0_6_df <- transform(zScore_MEpink_0_6_df_0_05, Color = Color.x)


zScore_MEdarkgreen_0_6_df_0_05 <- read_csv("zScore_MEdarkgreen_0_6_df_0.05.csv")

MEdarkgreen_0_6_df <- transform(zScore_MEdarkgreen_0_6_df_0_05, Color = Color.x)


zScore_MEdarkred_0_6_df_0_05 <- read_csv("zScore_MEdarkred_0_6_df_0.05.csv")

MEdarkred_0_6_df <- transform(zScore_MEdarkred_0_6_df_0_05, Color = Color.x)



zScore_MEpurple_0_6_df_0_05 <- read_csv("zScore_MEpurple_0_6_df_0.05.csv")

MEpurple_0_6_df <- transform(zScore_MEpurple_0_6_df_0_05, Color = Color.x)


colnames(MEpurple_0_6_df)



# Define the columns you want to keep
selected_columns <- c("GeneID", "Color.x", "gid", "cluster", "ReplicateGroup", "AvgExprs", "TCavg", "zScore")

# Function to read data, transform, select columns, and return
process_data <- function(file_path) {
  df <- read_csv(file_path)
  df <- transform(df, Color = Color.x)  # Create the Color column
  
  # Select only the desired columns.  Handle missing columns gracefully.
  df_selected <- df %>%
    select(any_of(selected_columns))  # Use any_of to avoid errors if a column is missing
  
  return(df_selected)
}

# Process each color
MEtan_0_6_df <- process_data("zScore_MEtan_0_6_df_0.05.csv")
MEpink_0_6_df <- process_data("zScore_MEpink_0_6_df_0.05.csv")
MEdarkgreen_0_6_df <- process_data("zScore_MEdarkgreen_0_6_df_0.05.csv")
MEdarkred_0_6_df <- process_data("zScore_MEdarkred_0_6_df_0.05.csv")
MEpurple_0_6_df <- process_data("zScore_MEpurple_0_6_df_0.05.csv")

# Bind all data frames
df_combined <- bind_rows(
  MEtan_0_6_df,
  MEpink_0_6_df,
  MEdarkgreen_0_6_df,
  MEdarkred_0_6_df,
  MEpurple_0_6_df
)

# Print the column names of the combined data frame to verify
print(colnames(df_combined))




df_combined$ReplicateGroup <- factor(df_combined$ReplicateGroup, levels = unique(df_combined$ReplicateGroup))


# Calculate mean and standard deviation for each replicate group
df_summary <- df_combined %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )

p <- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), fill = "blue", alpha = 0.2) +
  labs(title = "Average Z Score_Clade1",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )

# Print the plot
print(p)

# Save the plot with higher resolution
ggsave("high_resolution_plot.png", plot = p, width = 16, height = 14, dpi = 1200)



###Clade 2 

zScore_MEmagenta_0_6_df_0_05 <- read_csv("zScore_MEmagenta_0_6_df_0.05.csv")

MEmagenta_0_6_df <- transform(zScore_MEmagenta_0_6_df_0_05, Color = Color.x)


zScore_MEgreen_0_6_df_0_05 <- read_csv("zScore_MEgreen_0_6_df_0.05.csv")

MEgreen_0_6_df <- transform(zScore_MEgreen_0_6_df_0_05, Color = Color.x)


zScore_MEroyalblue_0_6_df_0_05 <- read_csv("zScore_MEroyalblue_0_6_df_0.05.csv")

MEroyalblue_0_6_df <- transform(zScore_MEroyalblue_0_6_df_0_05, Color = Color.x)


zScore_MEorange_0_6_df_0_05 <- read_csv("zScore_MEorange_0_6_df_0.05.csv")

MEorange_0_6_df <- transform(zScore_MEorange_0_6_df_0_05, Color = Color.x)



zScore_MElightcyan_0_6_df_0_05 <- read_csv("zScore_MElightcyan_0_6_df_0.05.csv")

MElightcyan_0_6_df <- transform(zScore_MElightcyan_0_6_df_0_05, Color = Color.x)

zScore_MEblue_0_6_df_0_05 <- read_csv("zScore_MEblue_0_6_df_0.05.csv")

MEblue_0_6_df <- transform(zScore_MEblue_0_6_df_0_05, Color = Color.x)

zScore_MElightyellow_0_6_df_0_05 <- read_csv("zScore_MElightyellow_0_6_df_0.05.csv")

MElightyellow_0_6_df <- transform(zScore_MElightyellow_0_6_df_0_05, Color = Color.x)


# Define the columns you want to keep
selected_columns <- c("GeneID", "Color.x", "gid", "cluster", "ReplicateGroup", "AvgExprs", "TCavg", "zScore")

# Function to read data, transform, select columns, and return
process_data <- function(file_path) {
  df <- read_csv(file_path)
  df <- transform(df, Color = Color.x)  # Create the Color column
  
  # Select only the desired columns.  Handle missing columns gracefully.
  df_selected <- df %>%
    select(any_of(selected_columns))  # Use any_of to avoid errors if a column is missing
  
  return(df_selected)
}

# Process each color
MEmagenta_0_6_df <- process_data("zScore_MEmagenta_0_6_df_0.05.csv")
MEgreen_0_6_df <- process_data("zScore_MEgreen_0_6_df_0.05.csv")
MEroyalblue_0_6_df <- process_data("zScore_MEroyalblue_0_6_df_0.05.csv")
MEorange_0_6_df <- process_data("zScore_MEorange_0_6_df_0.05.csv")
MElightcyan_0_6_df <- process_data("zScore_MElightcyan_0_6_df_0.05.csv")
MEblue_0_6_df <- process_data("zScore_MEblue_0_6_df_0.05.csv")
MElightyellow_0_6_df <- process_data("zScore_MElightyellow_0_6_df_0.05.csv")
# Bind all data frames
df_combined <- bind_rows(
  MEmagenta_0_6_df,
  MEgreen_0_6_df,
  MEroyalblue_0_6_df,
  MEorange_0_6_df,
  MElightcyan_0_6_df,
  MEblue_0_6_df,
  MElightyellow_0_6_df
)

# Print the column names of the combined data frame to verify
print(colnames(df_combined))




df_combined$ReplicateGroup <- factor(df_combined$ReplicateGroup, levels = unique(df_combined$ReplicateGroup))


# Calculate mean and smagentadard deviation for each replicate group
df_summary <- df_combined %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )

p <- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), fill = "red", alpha = 0.2) +
  labs(title = "Average Z Score_Clade2",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )

# Print the plot
print(p)

# Save the plot with higher resolution
ggsave("high_resolution_plot_clade2.png", plot = p, width = 16, height = 14, dpi = 1200)



#clade3

zScore_MEdarkorange_0_6_df_0_05 <- read_csv("zScore_MEdarkorange_0_6_df_0.05.csv")

MEdarkorange_0_6_df <- transform(zScore_MEdarkorange_0_6_df_0_05, Color = Color.x)


zScore_MEsalmon_0_6_df_0_05 <- read_csv("zScore_MEsalmon_0_6_df_0.05.csv")

MEsalmon_0_6_df <- transform(zScore_MEsalmon_0_6_df_0_05, Color = Color.x)


zScore_MEbrown_0_6_df_0_05 <- read_csv("zScore_MEbrown_0_6_df_0.05.csv")

MEbrown_0_6_df <- transform(zScore_MEbrown_0_6_df_0_05, Color = Color.x)


zScore_MEdarkgrey_0_6_df_0_05 <- read_csv("zScore_MEdarkgrey_0_6_df_0.05.csv")

MEdarkgrey_0_6_df <- transform(zScore_MEdarkgrey_0_6_df_0_05, Color = Color.x)




# Define the columns you want to keep
selected_columns <- c("GeneID", "Color.x", "gid", "cluster", "ReplicateGroup", "AvgExprs", "TCavg", "zScore")

# Function to read data, transform, select columns, and return
process_data <- function(file_path) {
  df <- read_csv(file_path)
  df <- transform(df, Color = Color.x)  # Create the Color column
  
  # Select only the desired columns.  Handle missing columns gracefully.
  df_selected <- df %>%
    select(any_of(selected_columns))  # Use any_of to avoid errors if a column is missing
  
  return(df_selected)
}

# Process each color
MEdarkorange_0_6_df <- process_data("zScore_MEdarkorange_0_6_df_0.05.csv")
MEsalmon_0_6_df <- process_data("zScore_MEsalmon_0_6_df_0.05.csv")
MEbrown_0_6_df <- process_data("zScore_MEbrown_0_6_df_0.05.csv")
MEdarkgrey_0_6_df <- process_data("zScore_MEdarkgrey_0_6_df_0.05.csv")

# Bind all data frames
df_combined <- bind_rows(
  MEdarkorange_0_6_df,
  MEsalmon_0_6_df,
  MEbrown_0_6_df,
  MEdarkgrey_0_6_df)

# Print the column names of the combined data frame to verify
print(colnames(df_combined))




df_combined$ReplicateGroup <- factor(df_combined$ReplicateGroup, levels = unique(df_combined$ReplicateGroup))


# Calculate mean and standard deviation for each replicate group
df_summary <- df_combined %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )

p <- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), fill = "darkgreen", alpha = 0.2) +
  labs(title = "Average Z Score_Clade3",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )

# Print the plot
print(p)

# Save the plot with higher resolution
ggsave("high_resolution_plot_clade3.png", plot = p, width = 16, height = 14, dpi = 1200)

zScore_MEcyan_0_6_df_0_05 <- read_csv("zScore_MEcyan_0_6_df_0.05.csv")

MEcyan_0_6_df <- transform(zScore_MEcyan_0_6_df_0_05, Color = Color.x)


zScore_MEgreenyellow_0_6_df_0_05 <- read_csv("zScore_MEgreenyellow_0_6_df_0.05.csv")

MEgreenyellow_0_6_df <- transform(zScore_MEgreenyellow_0_6_df_0_05, Color = Color.x)


zScore_MEyellow_0_6_df_0_05 <- read_csv("zScore_MEyellow_0_6_df_0.05.csv")

MEyellow_0_6_df <- transform(zScore_MEyellow_0_6_df_0_05, Color = Color.x)


zScore_MEdarkturquoise_0_6_df_0_05 <- read_csv("zScore_MEdarkturquoise_0_6_df_0.05.csv")

MEdarkturquoise_0_6_df <- transform(zScore_MEdarkturquoise_0_6_df_0_05, Color = Color.x)

zScore_MEred_0_6_df_0_05 <- read_csv("zScore_MEred_0_6_df_0.05.csv")

MEred_0_6_df <- transform(zScore_MEred_0_6_df_0_05, Color = Color.x)


# Define the columns you want to keep
selected_columns <- c("GeneID", "Color.x", "gid", "cluster", "ReplicateGroup", "AvgExprs", "TCavg", "zScore")

# Function to read data, transform, select columns, and return
process_data <- function(file_path) {
  df <- read_csv(file_path)
  df <- transform(df, Color = Color.x)  # Create the Color column
  
  # Select only the desired columns.  Handle missing columns gracefully.
  df_selected <- df %>%
    select(any_of(selected_columns))  # Use any_of to avoid errors if a column is missing
  
  return(df_selected)
}

# Process each color
MEcyan_0_6_df <- process_data("zScore_MEcyan_0_6_df_0.05.csv")
MEgreenyellow_0_6_df <- process_data("zScore_MEgreenyellow_0_6_df_0.05.csv")
MEyellow_0_6_df <- process_data("zScore_MEyellow_0_6_df_0.05.csv")
MEdarkturquoise_0_6_df <- process_data("zScore_MEdarkturquoise_0_6_df_0.05.csv")
MEred_0_6_df <- process_data("zScore_MEred_0_6_df_0.05.csv")
# Bind all data frames
df_combined <- bind_rows(
  MEcyan_0_6_df,
  MEgreenyellow_0_6_df,
  MEyellow_0_6_df,
  MEdarkturquoise_0_6_df,
  MEred_0_6_df,
)

# Print the column names of the combined data frame to verify
print(colnames(df_combined))




df_combined$ReplicateGroup <- factor(df_combined$ReplicateGroup, levels = unique(df_combined$ReplicateGroup))


# Calculate mean and standard deviation for each replicate group
df_summary <- df_combined %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )

p <- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), fill = "purple", alpha = 0.2) +
  labs(title = "Average Z Score_Clade4",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )

# Print the plot
print(p)

# Save the plot with higher resolution
ggsave("high_resolution_plot_clade4.png", plot = p, width = 16, height = 14, dpi = 1200)


#clade5

zScore_MEblack_0_6_df_0_05 <- read_csv("zScore_MEblack_0_6_df_0.05.csv")

MEblack_0_6_df <- transform(zScore_MEblack_0_6_df_0_05, Color = Color.x)


zScore_MEgrey60_0_6_df_0_05 <- read_csv("zScore_MEgrey60_0_6_df_0.05.csv")

MEgrey60_0_6_df <- transform(zScore_MEgrey60_0_6_df_0_05, Color = Color.x)


zScore_MEturquoise_0_6_df_0_05 <- read_csv("zScore_MEturquoise_0_6_df_0.05.csv")

MEturquoise_0_6_df <- transform(zScore_MEturquoise_0_6_df_0_05, Color = Color.x)


zScore_MElightgreen_0_6_df_0_05 <- read_csv("zScore_MElightgreen_0_6_df_0.05.csv")

MElightgreen_0_6_df <- transform(zScore_MElightgreen_0_6_df_0_05, Color = Color.x)

zScore_MEmidnightblue_0_6_df_0_05 <- read_csv("zScore_MEmidnightblue_0_6_df_0.05.csv")

MEmidnightblue_0_6_df <- transform(zScore_MEmidnightblue_0_6_df_0_05, Color = Color.x)


# Define the columns you want to keep
selected_columns <- c("GeneID", "Color.x", "gid", "cluster", "ReplicateGroup", "AvgExprs", "TCavg", "zScore")

# Function to read data, transform, select columns, and return
process_data <- function(file_path) {
  df <- read_csv(file_path)
  df <- transform(df, Color = Color.x)  # Create the Color column
  
  # Select only the desired columns.  Handle missing columns gracefully.
  df_selected <- df %>%
    select(any_of(selected_columns))  # Use any_of to avoid errors if a column is missing
  
  return(df_selected)
}

# Process each color
MEblack_0_6_df <- process_data("zScore_MEblack_0_6_df_0.05.csv")
MEgrey60_0_6_df <- process_data("zScore_MEgrey60_0_6_df_0.05.csv")
MEturquoise_0_6_df <- process_data("zScore_MEturquoise_0_6_df_0.05.csv")
MElightgreen_0_6_df <- process_data("zScore_MElightgreen_0_6_df_0.05.csv")
MEmidnightblue_0_6_df <- process_data("zScore_MEmidnightblue_0_6_df_0.05.csv")
# Bind all data frames
df_combined <- bind_rows(
  MEblack_0_6_df,
  MEgrey60_0_6_df,
  MEturquoise_0_6_df,
  MElightgreen_0_6_df,
  MEmidnightblue_0_6_df,
)

# Print the column names of the combined data frame to verify
print(colnames(df_combined))




df_combined$ReplicateGroup <- factor(df_combined$ReplicateGroup, levels = unique(df_combined$ReplicateGroup))


# Calculate mean and standard deviation for each replicate group
df_summary <- df_combined %>%
  group_by(ReplicateGroup) %>%
  summarise(
    mean_Zscore = mean(zScore, na.rm = TRUE),
    sd_Zscore = sd(zScore, na.rm = TRUE)
  )

p <- ggplot(df_summary, aes(x = ReplicateGroup, y = mean_Zscore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_Zscore - sd_Zscore, ymax = mean_Zscore + sd_Zscore), fill = "darkturquoise", alpha = 0.2) +
  labs(title = "Average Z Score_Clade5",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )

# Print the plot
print(p)

# Save the plot with higher resolution
ggsave("high_resolution_plot_clade5.png", plot = p, width = 16, height = 14, dpi = 1200)
```

Clade GO enrichment (Figure 3 A)

```{r}
setwd("~/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster")


library(readr)


Gene_Clade_consolidated_0_6MM_frame <- read_csv("Gene_Clade_consolidated_0.6MM_frame.csv")


library(clusterProfiler)
library(dplyr)
library(readxl)
library(tidyr) 
library(org.At.tair.db)
library(ggplot2)
# Read the data from an Excel file
# Replace 'your_file.xlsx' with the path to your actual file
data <- read_csv("Gene_Clade_consolidated_0.6MM_frame.csv")

# Clean data: Remove rows where Gene is NA
data <- data %>% filter(!is.na(Gene))

# Melt the data frame to long format to retain cluster information
data_long <- data %>%
  pivot_longer(cols = starts_with("Cluster"), 
               names_to = "Cluster", 
               values_to = "Clade") %>%
  filter(!is.na(Clade))  # Remove NA values

# Group by Clade
clades <- data_long %>% group_by(Clade) %>% summarise(Genes = list(Gene))

# Define a function to run GO enrichment analysis
run_go_analysis <- function(modules) {
  go_results <- enrichGO(gene = modules,
                         OrgDb = org.At.tair.db,  # Arabidopsis database
                         keyType = "TAIR",
                         ont = "ALL",  # Biological Process
                         pAdjustMethod = "BH",
                         qvalueCutoff = 0.05,
                         readable = TRUE)
  return(go_results)
}

# Run GO analysis for each clade and store results
results <- list()
for (i in seq_along(clades$Clade)) {
  clade <- clades$Clade[i]
  modules <- clades$Genes[[i]]
  
  cat("Running GO analysis for", clade, "...\n")
  results[[clade]] <- run_go_analysis(modules)
  
  # Save each GO result as a CSV file
  write.csv(as.data.frame(results[[clade]]), file = paste0(clade, "_GO_results_ALL.csv"), row.names = FALSE)
}

# Create and save graphs for each clade's GO results
for (clade in names(results)) {
  go_data <- as.data.frame(results[[clade]])
  
  # Create a bar plot for the top 10 GO terms
  plot <- ggplot(go_data[1:10, ], aes(x = reorder(Description, -Count), y = Count)) +
    geom_bar(stat = "identity", fill = "steelblue") +
    coord_flip() +
    labs(title = paste("Top 10 GO Terms for", clade),
         x = "GO Terms",
         y = "Gene Count") +
    theme_minimal()
  
  # Save the plot
  ggsave(filename = paste0(clade, "_GO_enrichment_plot_ALL.png"), plot = plot, width = 8, height = 6)
}


#####################################

##Finding Common GO terms between clades 


# Required packages
library(clusterProfiler)
library(dplyr)
library(readxl)
library(tidyr)
library(ggplot2)

# Read the data from an Excel file
data <- read_csv("Gene_Clade_consolidated_0.6MM_frame.csv")

# Clean data: Remove rows where Gene is NA
data <- data %>% filter(!is.na(Gene))

# Melt the data frame to long format to retain cluster information
data_long <- data %>%
  pivot_longer(cols = starts_with("Cluster"), 
               names_to = "Cluster", 
               values_to = "Clade") %>%
  filter(!is.na(Clade))  # Remove NA values

# Group by Clade
clades <- data_long %>% group_by(Clade) %>% summarise(Genes = list(Gene))

# Define a function to run GO enrichment analysis
run_go_analysis <- function(modules) {
  go_results <- enrichGO(gene = modules,
                         OrgDb = org.At.tair.db,  # Arabidopsis database
                         keyType = "TAIR",
                         ont = "ALL",  # Biological Process
                         pAdjustMethod = "BH",
                         qvalueCutoff = 0.05,
                         readable = TRUE)
  return(go_results)
}

# Run GO analysis for each clade and store results
results <- list()
for (i in seq_along(clades$Clade)) {
  clade <- clades$Clade[i]
  modules <- clades$Genes[[i]]
  
  cat("Running GO analysis for", clade, "...\n")
  results[[clade]] <- run_go_analysis(modules)
  
  # Save each GO result as a CSV file
  write.csv(as.data.frame(results[[clade]]), file = paste0(clade, "_GO_results_ALL.csv"), row.names = FALSE)
}

# Create a list to store GO terms across clades
go_terms_list <- lapply(results, function(res) as.data.frame(res)$ID)

# Function to find common GO terms for given clade combinations
find_common_go_terms <- function(clade_indices) {
  common_terms <- Reduce(intersect, go_terms_list[clade_indices])
  return(common_terms)
}

# Create a data frame to store common GO terms for different combinations
common_go_data <- data.frame(Clade_Combination = character(),
                             GO_ID = character(),
                             Description = character(),
                             stringsAsFactors = FALSE)

# Check common GO terms for combinations of 2 to 5 clades
for (n in 2:length(results)) {
  combos <- combn(seq_along(results), n)
  
  for (i in 1:ncol(combos)) {
    common_terms <- find_common_go_terms(combos[, i])
    
    for (go_id in common_terms) {
      description <- unique(unlist(lapply(combos[, i], function(clade_index) {
        as.data.frame(results[[clade_index]])$Description[as.data.frame(results[[clade_index]])$ID == go_id]
      })))
      
      common_go_data <- rbind(common_go_data, 
                              data.frame(Clade_Combination = paste(combos[, i], collapse = ", "),
                                         GO_ID = go_id,
                                         Description = description,
                                         stringsAsFactors = FALSE))
    }
  }
}

# Save the common GO terms data to a CSV file
write.csv(common_go_data, "common_GO_terms_combinations.csv", row.names = FALSE)

# Output common GO terms for various combinations
cat("Common GO Terms for Clade Combinations:\n")
print(common_go_data)


#saving result list as data frame

# Convert results list to a data frame, including gene information
all_go_data <- do.call(rbind, lapply(names(results), function(clade_name) {
  go_data <- as.data.frame(results[[clade_name]])
  
  # Add a new column for Clade
  go_data$Clade <- clade_name
  
  # Retrieve gene information for the specific clade
  gene_info <- clades$Genes[[which(clades$Clade == clade_name)]]
  
  # Create a string of genes for each GO term (if necessary)
  go_data$Genes <- paste(gene_info, collapse = ", ")
  
  return(go_data)
}))

library(dplyr)  # Ensure dplyr is loaded
library(tibble) # Load tibble package

# Convert all_go_data to a tibble

all_go_data <- as_tibble(all_go_data)


# Save the complete GO data frame to a CSV file
write.csv(all_go_data, "all_GO_terms_with_clade_and_gene_info.csv", row.names = FALSE)
```

Propotional_Clade_Cluster_data

```{r}
setwd("~/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster")

library(tidyverse)
Gene_Clade_consolidated_0_6MM_frame <- read_csv("Gene_Clade_consolidated_0.6MM_frame.csv")


# Load necessary libraries
library(dplyr)
library(reshape2)
library(ggplot2)

# View the first few rows of your data frame
head(Gene_Clade_consolidated_0_6MM_frame)
colnames(Gene_Clade_consolidated_0_6MM_frame)
new_names <- c("Gene", "c0", "c1", "c5", "c2", "c11", "c3", "c4", "c12_2", "c10", "c9", "c14", "c6", "c12_0", "c7", "c8_0", "c12_1", "c13", "c8_1", "c15")

colnames(Gene_Clade_consolidated_0_6MM_frame) = new_names

colnames(Gene_Clade_consolidated_0_6MM_frame)
desired_order <- c("Gene", "c0", "c1", "c2", "c3", "c4", "c5", "c6", "c7", "c8_0", "c8_1", "c9", "c10", "c11", "c12_0", "c12_1", "c12_2", "c13", "c14", "c15")
colnames(Gene_Clade_consolidated_0_6MM_frame)
# Reorder the columns of the data frame
Gene_Clade_consolidated_0_6MM_frame <- Gene_Clade_consolidated_0_6MM_frame[, desired_order]

# 1. Count the number of genes assigned to each cluster-clade combination
# Melt the data frame into a long format
long_data <- Gene_Clade_consolidated_0_6MM_frame %>%
  melt(id.vars = "Gene", variable.name = "Cluster", value.name = "Clade") %>%
  filter(!is.na(Clade))  # Remove rows where Clade is NA

# Count the number of genes per cluster and clade
cluster_clade_counts <- long_data %>%
  group_by(Cluster, Clade) %>%
  summarise(GeneCount = n(), .groups = "drop")

# Display the cluster-clade gene counts
print(cluster_clade_counts)

# 2. Visualize the distribution of genes across clusters and clades
# Define a color palette for the clades
clade_colors <- c(
  "Clade1" = "#99AAEC",
  "Clade2" = "pink",
  "Clade3" = "#A6D870",
  "Clade4" = "#CBA7E8",
  "Clade5" = "#92F1EF"
  # Add more clades and colors as needed
)

# Calculate proportions within each cluster
cluster_clade_proportions <- cluster_clade_counts %>%
  group_by(Cluster) %>%
  mutate(Proportion = GeneCount / sum(GeneCount)) %>%
  ungroup()

# Create the proportional bar plot
my_plot <- ggplot(cluster_clade_proportions, aes(x = Cluster, y = Proportion, fill = Clade)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = clade_colors) +  # Apply the color palette
  labs(
    title = "Proportional Distribution of Genes Across Clusters and Clades",
    x = "Cluster",
    y = "Proportion of Genes"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.title.x = element_text(size = 14),
    axis.text.y = element_text(size = 12),
    axis.title.y = element_text(size = 14),
    title = element_text(size = 16, hjust = 0.5)
  ) +
  # Add gene counts on top of each bar segment
  geom_text(aes(label = GeneCount), 
            position = position_stack(vjust = 0.5),
            size = 3) # Adjust size as needed

# Save the plot as a PNG file:
ggsave("cluster_clade_proportional_distribution_with_counts_propotional_data_menuscript_data.png", plot = my_plot, width = 10, height = 6, units = "in", dpi = 600)

```

Figure 3 C

```{r}
setwd("~/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster")

library(tidyverse)


Gene_Clade_consolidated_0_6MM_frame <- read_csv("Gene_Clade_consolidated_0.6MM_frame.csv")



# Load necessary libraries
library(dplyr)
library(reshape2)
library(ggplot2)

# View the first few rows of your data frame
head(Gene_Clade_consolidated_0_6MM_frame)

# 1. Count the number of genes assigned to each cluster-clade combination
# Melt the data frame into a long format
long_data <- Gene_Clade_consolidated_0_6MM_frame %>%
  melt(id.vars = "Gene", variable.name = "Cluster", value.name = "Clade") %>%
  filter(!is.na(Clade))  # Remove rows where Clade is NA

# Count the number of genes per cluster and clade
cluster_clade_counts <- long_data %>%
  group_by(Cluster, Clade) %>%
  summarise(GeneCount = n(), .groups = "drop")

# Display the cluster-clade gene counts
print(cluster_clade_counts)

# 2. Visualize the distribution of genes across clusters and clades
# Define a color palette for the clades
clade_colors <- c(
  "Clade1" = "#99AAEC",
  "Clade2" = "pink",
  "Clade3" = "#A6D870",
  "Clade4" = "#CBA7E8",
  "Clade5" = "#92F1EF"
  # Add more clades and colors as needed
)

my_plot <- ggplot(cluster_clade_counts, aes(x = Cluster, y = GeneCount, fill = Clade)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = clade_colors) +  # Apply the color palette
  labs(
    title = "Distribution of Genes Across Clusters and Clades",
    x = "Cluster",
    y = "Number of Genes"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12), # Increase x-axis label font size
    axis.title.x = element_text(size = 14),                         # Increase x-axis title font size
    axis.text.y = element_text(size = 12),                         # Increase y-axis label font size
    axis.title.y = element_text(size = 14),                         # Increase y-axis title font size
    title = element_text(size = 16, hjust = 0.5)                   # Increase title font size and center it
  )

# Save the plot as a PNG file:
ggsave("cluster_clade_distribution.png", plot = my_plot, width = 10, height = 6, units = "in", dpi = 600)



# Count the number of distinct clades for each gene
genes_in_multiple_clades <- long_data %>%
  group_by(Gene) %>%
  summarize(CladeCount = n_distinct(Clade), .groups = "drop") %>%
  filter(CladeCount >= 2)  # Filter for genes present in two or more clades

# View the result
print(genes_in_multiple_clades)

# Group by Gene and concatenate Cluster and Clade values
result_df <- long_data %>%
  group_by(Gene) %>%
  summarize(
    Clusters = paste(unique(Cluster), collapse = ", "),
    Clades = paste(unique(Clade), collapse = ", "),
    .groups = "drop"
  )

# View the result
print(result_df)

write_csv(result_df, "new_genes_in_multiple_clades.csv")
################

# Load necessary libraries
library(dplyr)
library(tidyr)

# Assuming your data frame is named df_clean
# Split the Clades into separate rows and count the number of clades per gene
df_separated <- result_df %>%
  separate_rows(Clades, sep = ", ") %>%
  group_by(Gene) %>%
  mutate(CladeCount = n_distinct(Clades)) %>%
  ungroup()

# Create sub-data frames based on the number of clades
genes_in_1_clade <- df_separated %>%
  filter(CladeCount == 1) %>%
  distinct(Gene, Clades)

# Assuming df_separated is already created and includes CladeCount
# Group by Gene and concatenate Clades into a single string
genes_in_2_clades <- df_separated %>%
  filter(CladeCount == 2) %>%
  group_by(Gene) %>%
  summarise(Clades = paste(unique(Clades), collapse = ", "), .groups = "drop")

genes_in_3_clades <- df_separated %>%
  filter(CladeCount == 3) %>%
  group_by(Gene) %>%
  summarise(Clades = paste(unique(Clades), collapse = ", "), .groups = "drop")


# You can continue this for more clade counts as needed
# For example, for up to 4 clades
genes_in_4_clades <- df_separated %>%
  filter(CladeCount == 4) %>%
  group_by(Gene) %>%
  summarise(Clades = paste(unique(Clades), collapse = ", "), .groups = "drop")

########################################


genes_in_2_clades <- df_separated %>%
  filter(CladeCount == 2) %>%
  group_by(Gene) %>%
  summarise(Clades = paste(unique(Clades), collapse = ", "), .groups = "drop")

# Create the adjacency matrix
adjacency_data <- genes_in_2_clades %>%
  mutate(Clades = str_split(Clades, ", ")) %>%
  unnest(Clades) %>%
  count(Gene, Clades) %>%
  spread(Clades, n, fill = 0)

# Define the adjacency matrix
adj_matrix <- as.matrix(adjacency_data[,-1])  # Remove Gene column for matrix




# Set row names
rownames(adj_matrix) <- df_separated$Gene

adj_matrix <- data.frame(adj_matrix)

# Summarize gene counts for each combination of clades
summary_data <- as.data.frame(table(
  Clade1 = rowSums(adj_matrix[, 1:5] == 1) > 0,
  Clade2 = rowSums(adj_matrix[, 1:5] == 1) > 0
))


# Calculate the counts for combinations of clades
Count <- c(
  sum(adj_matrix$Clade1 == 1 & adj_matrix$Clade2 == 1),
  sum(adj_matrix$Clade1 == 1 & adj_matrix$Clade3 == 1),
  sum(adj_matrix$Clade1 == 1 & adj_matrix$Clade4 == 1),
  sum(adj_matrix$Clade1 == 1 & adj_matrix$Clade5 == 1),
  sum(adj_matrix$Clade2 == 1 & adj_matrix$Clade3 == 1),
  sum(adj_matrix$Clade2 == 1 & adj_matrix$Clade4 == 1),
  sum(adj_matrix$Clade2 == 1 & adj_matrix$Clade5 == 1),
  sum(adj_matrix$Clade3 == 1 & adj_matrix$Clade4 == 1),
  sum(adj_matrix$Clade3 == 1 & adj_matrix$Clade5 == 1),
  sum(adj_matrix$Clade4 == 1 & adj_matrix$Clade5 == 1)
)

# Create a data frame for Circos plot
circus_data <- data.frame(
  Clades = c("Clade1 & Clade2", "Clade1 & Clade3", "Clade1 & Clade4", "Clade1 & Clade5",
             "Clade2 & Clade3", "Clade2 & Clade4", "Clade2 & Clade5",
             "Clade3 & Clade4", "Clade3 & Clade5", "Clade4 & Clade5"),
  Count = Count
)


# Split the Clades into separate columns
clade_split <- do.call(rbind, strsplit(circus_data$Clades, " & "))

# Create a unique list of clades
unique_clades <- unique(c(clade_split))

# Initialize a square matrix
square_matrix <- matrix(0, nrow = length(unique_clades), ncol = length(unique_clades),
                        dimnames = list(unique_clades, unique_clades))

# Fill in the matrix with counts
for (i in 1:nrow(circus_data)) {
  clades <- clade_split[i, ]
  square_matrix[clades[1], clades[2]] <- circus_data$Count[i]
  square_matrix[clades[2], clades[1]] <- circus_data$Count[i]  # Fill the opposite direction
}

# View the resulting square matrix
print(square_matrix)
# Convert the matrix to a data frame for writing
square_matrix_df <- as.data.frame(square_matrix)
# Add row names as a column
square_matrix_df$Clades <- rownames(square_matrix_df)

# Reorder columns to have Clades first
square_matrix_df <- square_matrix_df[, c(ncol(square_matrix_df), 1:(ncol(square_matrix_df) - 1))]

# Write to CSV
write_csv(square_matrix_df, "square_matrix_genes_in_2_clades.csv")
Reset_data_frame_square_matrix_genes_in_2_clades <- read_excel("Reset_data_frame_square_matrix_genes_in_2_clades.xlsx")


# Assuming square_matrix_genes_in_2_clades is already defined
Reset_data_frame_square_matrix_genes_in_2_clades <- as.data.frame(Reset_data_frame_square_matrix_genes_in_2_clades)

# Remove the 'Clades' column by selecting all other columns
Reset_data_frame_square_matrix_genes_in_2_clades_df <- Reset_data_frame_square_matrix_genes_in_2_clades[, -1]

Reset_data_frame_square_matrix_genes_in_2_clades_df

# Set row names
rownames(Reset_data_frame_square_matrix_genes_in_2_clades_df) <- Reset_data_frame_square_matrix_genes_in_2_clades$Clades

# Load the required library
library(circlize)

# Assuming square_matrix_genes_in_2_clades_df is your data frame
# Convert to matrix (excluding row names)
square_matrix_genes_in_2_clades_matrix <- as.matrix(Reset_data_frame_square_matrix_genes_in_2_clades_df)

# Ensure the row and column names are set correctly
rownames(square_matrix_genes_in_2_clades_matrix) <- colnames(Reset_data_frame_square_matrix_genes_in_2_clades)


circos.clear()
circos.clear()

# Define color for each clade
clade_colors <- c("Clade1" = "#99AAEC", "Clade2" = "pink",
                  "Clade3" = "#A6D870", "Clade4" = "#CBA7E8",
                  "Clade5" = "#92F1EF")
# Create the chord diagram
chordDiagram(square_matrix_genes_in_2_clades_matrix, grid.col = clade_colors)


# Define the order of sectors (clades)
sector_order <- c("Clade3", "Clade2", "Clade1", "Clade4", "Clade5")
chordDiagram(square_matrix_genes_in_2_clades_matrix, grid.col = clade_colors, order = sector_order)


# Add title
title("Circos Plot of Gene Combinations Between Clades")

```

Combinations of gene in different clades from same clusters


```{r}
setwd("~/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster")

library(tidyverse)


Gene_Clade_consolidated_0_6MM_frame <- read_csv("Gene_Clade_consolidated_0.6MM_frame.csv")



# Load necessary libraries
library(dplyr)
library(reshape2)
library(ggplot2)


# Function to subset genes in specific clades from specified clusters
subset_genes_all <- function(df, clades, clusters) {
  results <- list()
  
  # Loop through each specified cluster
  for (cluster in clusters) {
    if (cluster %in% names(df)) {
      # Filter for specified clades in the current cluster
      clade_data <- df %>%
        filter(!!sym(cluster) %in% clades) %>%
        select(Gene, !!sym(cluster))
      
      if (nrow(clade_data) > 0) {
        # Ensure the column names are consistent
        colnames(clade_data) <- c("Gene", "Clade")
        results[[cluster]] <- clade_data
      } else {
        warning(paste("No genes found in", cluster, "for specified clades."))
      }
    } else {
      warning(paste("Cluster name", cluster, "not found in data frame."))
    }
  }
  
  # Combine results from specified clusters
  if (length(results) > 0) {
    combined_results <- do.call(rbind, results)
    # Find genes that are present in both clades across the specified clusters
    gene_counts <- combined_results %>%
      group_by(Gene) %>%
      summarize(CladeCount = n_distinct(Clade)) %>%
      filter(CladeCount == length(clades))
    
    # Return the final subset of genes
    return(gene_counts$Gene)
  } else {
    return(character())  # Return an empty character vector if no results
  }
}

# Specify clades and clusters
clades_to_find <- c('Clade2', 'Clade5')  # Clades to check
clusters_to_check <- c('Cluster1', 'Cluster10')  # Specified clusters

# Get subset of genes
subset_result <- subset_genes_all(Gene_Clade_consolidated_0_6MM_frame, clades_to_find, clusters_to_check)
print(subset_result)



#####Clade3 and Clade 2


# Specify clades and clusters
clades_to_find <- c('Clade3', 'Clade2')  # Clades to check
clusters_to_check <- c('Cluster1', 'Cluster10')  # Specified clusters

# Get subset of genes
subset_result <- subset_genes_all(Gene_Clade_consolidated_0_6MM_frame, clades_to_find, clusters_to_check)
print(subset_result)


##########


# Specify clades and clusters
clades_to_find <- c('Clade5', 'Clade4')  # Clades to check
clusters_to_check <- c('Cluster1', 'Cluster10')  # Specified clusters

# Get subset of genes
subset_result <- subset_genes_all(Gene_Clade_consolidated_0_6MM_frame, clades_to_find, clusters_to_check)
print(subset_result)


# Specify clades and clusters
clades_to_find <- c('Clade1', 'Clade2')  # Clades to check
clusters_to_check <- c('Cluster1', 'Cluster10')  # Specified clusters

# Get subset of genes
subset_result <- subset_genes_all(Gene_Clade_consolidated_0_6MM_frame, clades_to_find, clusters_to_check)
print(subset_result)
```

Figure 3 D


```{r}
setwd("~/Desktop/Mirror/JTK_GIDS_Modified_Data/12312024_Cluster_split_data/MetacycleDeSeq_Normalised_Cluster")


# Load necessary libraries
library(dplyr)
library(ggplot2)
library(readr)




# Create a data frame for specified genes and their module colors for Clade 3 and clade 5
gene_module_colors <- data.frame(
  Gene = c("AT1G44000_1", "AT1G73870_1", "AT2G41250_1", "AT2G46830_1", "AT3G02380_1","AT3G13040_1", "AT4G16990_1", "AT5G45430_1", "AT5G64940_1",
           "AT1G44000_10", "AT1G73870_10", "AT2G41250_10", "AT2G46830_10", "AT3G02380_10", "AT3G13040_10", "AT4G16990_10", "AT5G45430_10", "AT5G64940_10"),
  Clade5_Color = c("turquoise", "black", "black", "black", "black", "black","turquoise", "turquoise","turquoise",NA, NA, NA, NA, NA, NA, NA, NA, NA),
  clade3_Color = c(NA, NA, NA, NA, NA, NA, NA, NA, NA, "salmon", "salmon", "salmon", "salmon", "brown", "brown", "brown", "brown", "salmon"),
  stringsAsFactors = FALSE
)

# Extract unique colors for file names
colors <- unique(c(gene_module_colors$Clade5_Color[!is.na(gene_module_colors$Clade5_Color)],
                   gene_module_colors$clade3_Color[!is.na(gene_module_colors$clade3_Color)]))

# Create a mapping of colors to file names
color_file_mapping <- list(
  turquoise = "zScore_MEturquoise_0_6_df_0.05.csv",
  black = "zScore_MEblack_0_6_df_0.05.csv",
  salmon = "zScore_MEsalmon_0_6_df_0.05.csv",
  brown = "zScore_MEbrown_0_6_df_0.05.csv"
)

# Function to read data, transform, select columns, and return
process_data <- function(file_path, genes_of_interest) {
  df <- read_csv(file_path)
  df <- transform(df, Color = Color.x)  # Create the Color column
  
  # Select only the desired columns. Handle missing columns gracefully.
  selected_columns <- c("GeneID", "Color.x", "gid", "cluster", "ReplicateGroup", "AvgExprs", "TCavg", "zScore", "TCsd")
  df_selected <- df %>%
    select(any_of(selected_columns)) %>%
    filter(GeneID %in% genes_of_interest)  # Filter for specified genes
  
  return(df_selected)
}

# Read and process each color dataset based on the mapping
genes_of_interest_clade5 <- gene_module_colors$Gene[grepl("_1$", gene_module_colors$Gene)]
genes_of_interest_clade3 <- gene_module_colors$Gene[grepl("_10$", gene_module_colors$Gene)]

# Process data according to the colors
MEturquoise_0_6_df <- process_data(color_file_mapping[["turquoise"]], genes_of_interest_clade5)
MEblack_0_6_df <- process_data(color_file_mapping[["black"]], genes_of_interest_clade5)
MEsalmon_0_6_df <- process_data(color_file_mapping[["salmon"]], genes_of_interest_clade3)
MEbrown_0_6_df <- process_data(color_file_mapping[["brown"]], genes_of_interest_clade3)

# Bind all data frames
df_combined <- bind_rows(
  MEturquoise_0_6_df,
  MEblack_0_6_df,
  MEsalmon_0_6_df,
  MEbrown_0_6_df
)

# Print the column names of the combined data frame to verify
print(colnames(df_combined))

# Ensure ReplicateGroup is a factor
df_combined$ReplicateGroup <- factor(df_combined$ReplicateGroup, levels = unique(df_combined$ReplicateGroup))

# Separate data for Clade 3 and clade 5
df_clade3 <- df_combined %>% filter(Color.x %in% gene_module_colors$clade3_Color)
df_clade5 <- df_combined %>% filter(Color.x %in% gene_module_colors$Clade5_Color)


# Load necessary library
library(dplyr)

# Remove duplicate rows from df_clade3
df_clade3_unique <- df_clade3 %>% distinct()

# If you want to keep it in the original df_clade3 variable
df_clade3 <- df_clade3 %>% distinct()

df <- df_clade3

# Assuming your data frame is named 'df_summary'
# Step 1: Summarize the data to get the mean Z score and standard deviation
mean_z_scores <- df %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup()



p <- ggplot(mean_z_scores, aes(x = ReplicateGroup, y = mean_zScore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore), fill = "#A6D870", alpha = 0.2) +
  labs(title = "Six Genes within Clade 3",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )
p



df2 <- df_clade5

# Assuming your data frame is named 'df_summary'
# Step 1: Summarize the data to get the mean Z score and standard deviation
mean_z_scores2 <- df2 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup()



p2 <- ggplot(mean_z_scores2, aes(x = ReplicateGroup, y = mean_zScore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore), fill = "darkturquoise", alpha = 0.2) +
  labs(title = "Six Genes within Clade 3",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )
p2


# Summarize the data for Clade 3
mean_z_scores_clade3 <- df_clade3 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Clade = "Clade 3")

# Summarize the data for Clade 5
mean_z_scores_clade5 <- df_clade5 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Clade = "Clade 5")


# Combine the summaries into one data frame
mean_z_scores_combined <- bind_rows(mean_z_scores_clade3, mean_z_scores_clade5)

# Define your colors for each clade
clade_colors <- c(
  "Clade 3" = "#A6D870",  # Example color for Clade3
  "Clade 5" = "darkturquoise"   # Example color for Clade5
)


p <- ggplot(mean_z_scores_combined, aes(x = ReplicateGroup, y = mean_zScore, group = Clade, color = Clade)) +
  
  geom_line(size = 1) +
  
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore, fill = Clade), alpha = 0.2) +
  
  labs(title = "Mean zScores for Clade 3 and Clade 5 of Nine Genes",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  
  theme_minimal() +
  
  theme(
    axis.title = element_text(size = 14, face = "bold"),       # Axis titles
    axis.text = element_text(size = 12, face = "bold"),        # Axis text
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5)  # Plot title (centered)
  ) +
  
  # Specify colors for both lines and ribbons
  scale_color_manual(values = clade_colors) +  # Set colors for lines
  scale_fill_manual(values = clade_colors)      # Set colors for ribbons

# Print the combined plot
print(p)

# Create a data frame for specified genes and their module colors for clade 2 and clade 5
gene_module_colors <- data.frame(
  Gene = c("AT1G06040_1", "AT1G31330_1", "AT2G25080_1", "AT3G21400_1", "AT5G28060_1", "AT5G58870_1",
           "AT1G06040_11", "AT1G31330_11", "AT2G25080_11", "AT3G21400_11", "AT5G28060_11", "AT5G58870_11"),
  Clade5_Color = c("black", "black", "black", "turquoise", "black", "turquoise", NA, NA, NA, NA, NA, NA),
  Clade2_Color = c(NA, NA, NA, NA, NA, NA, "blue", "blue", "blue", "lightcyan", "blue", "blue"),
  stringsAsFactors = FALSE
)

# Extract unique colors for file names
colors <- unique(c(gene_module_colors$Clade5_Color[!is.na(gene_module_colors$Clade5_Color)],
                   gene_module_colors$Clade2_Color[!is.na(gene_module_colors$Clade2_Color)]))

# Create a mapping of colors to file names
color_file_mapping <- list(
  black = "zScore_MEblack_0_6_df_0.05.csv",
  blue = "zScore_MEblue_0_6_df_0.05.csv",
  turquoise = "zScore_MEturquoise_0_6_df_0.05.csv",
  lightcyan = "zScore_MElightcyan_0_6_df_0.05.csv",
  blue = "zScore_MEblue_0_6_df_0.05.csv"
)

# Function to read data, transform, select columns, and return
process_data <- function(file_path, genes_of_interest) {
  df <- read_csv(file_path)
  df <- transform(df, Color = Color.x)  # Create the Color column
  
  # Select only the desired columns. Handle missing columns gracefully.
  selected_columns <- c("GeneID", "Color.x", "gid", "cluster", "ReplicateGroup", "AvgExprs", "TCavg", "zScore", "TCsd")
  df_selected <- df %>%
    select(any_of(selected_columns)) %>%
    filter(GeneID %in% genes_of_interest)  # Filter for specified genes
  
  return(df_selected)
}

# Read and process each color dataset based on the mapping
genes_of_interest_clade5 <- gene_module_colors$Gene[grepl("_1$", gene_module_colors$Gene)]
genes_of_interest_clade2 <- gene_module_colors$Gene[grepl("_11$", gene_module_colors$Gene)]

# Process data according to the colors
MEblack_0_6_df <- process_data(color_file_mapping[["black"]], genes_of_interest_clade5)
MEblue_0_6_df <- process_data(color_file_mapping[["blue"]], genes_of_interest_clade2)
MEturquoise_0_6_df <- process_data(color_file_mapping[["turquoise"]], genes_of_interest_clade5)
MElightcyan_0_6_df <- process_data(color_file_mapping[["lightcyan"]], genes_of_interest_clade2)
MEblue_0_6_df <- process_data(color_file_mapping[["blue"]], genes_of_interest_clade2)

# Bind all data frames
df_combined <- bind_rows(
  MEblack_0_6_df,
  MEblue_0_6_df,
  MEturquoise_0_6_df,
  MElightcyan_0_6_df,
  MEblue_0_6_df
)

# Print the column names of the combined data frame to verify
print(colnames(df_combined))

# Ensure ReplicateGroup is a factor
df_combined$ReplicateGroup <- factor(df_combined$ReplicateGroup, levels = unique(df_combined$ReplicateGroup))

# Separate data for clade 2 and clade 5
df_clade2 <- df_combined %>% filter(Color.x %in% gene_module_colors$Clade2_Color)
df_clade5 <- df_combined %>% filter(Color.x %in% gene_module_colors$Clade5_Color)


# Load necessary library
library(dplyr)

# Remove duplicate rows from df_clade2
df_clade2_unique <- df_clade2 %>% distinct()

# If you want to keep it in the original df_clade2 variable
df_clade2 <- df_clade2 %>% distinct()

df <- df_clade2

# Assuming your data frame is named 'df_summary'
# Step 1: Summarize the data to get the mean Z score and standard deviation
mean_z_scores <- df %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup()



p <- ggplot(mean_z_scores, aes(x = ReplicateGroup, y = mean_zScore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore), fill = "red", alpha = 0.2) +
  labs(title = "Six Genes within Clade 2",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )
p



df2 <- df_clade5

# Assuming your data frame is named 'df_summary'
# Step 1: Summarize the data to get the mean Z score and standard deviation
mean_z_scores2 <- df2 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup()



p2 <- ggplot(mean_z_scores2, aes(x = ReplicateGroup, y = mean_zScore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore), fill = "darkturquoise", alpha = 0.2) +
  labs(title = "Six Genes within Clade 2",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )
p2


# Summarize the data for Clade 2
mean_z_scores_clade2 <- df_clade2 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Clade = "Clade 2")

# Summarize the data for Clade 5
mean_z_scores_clade5 <- df_clade5 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Clade = "Clade 5")


# Combine the summaries into one data frame
mean_z_scores_combined <- bind_rows(mean_z_scores_clade2, mean_z_scores_clade5)

# Plot both datasets together
p <- ggplot(mean_z_scores_combined, aes(x = ReplicateGroup, y = mean_zScore, group = Clade, color = Clade)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore, fill = Clade), alpha = 0.2) +
  labs(title = "Mean zScores for Clade 2 and Clade 5 of six Genes",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 14, face = "bold"),       # Axis titles
    axis.text = element_text(size = 12, face = "bold"),        # Axis text
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5)  # Plot title (centered)
  )

# Print the combined plot
print(p)

############################################################



# Create a data frame for specified genes and their module colors for clade 4 and clade 1
gene_module_colors <- data.frame(
  Gene = c("AT2G35370_1", "AT3G11170_1", "AT4G10920_1", "AT4G17090_1", "AT4G21990_1", "AT5G56650_1",
           "AT2G35370_11", "AT3G11170_11", "AT4G10920_11", "AT4G17090_11", "AT4G21990_11", "AT5G56650_11"),
  clade4_Color = c("yellow", "yellow", "red", "greenyellow", "red", "greenyellow", NA, NA, NA, NA, NA, NA),
  clade1_Color = c(NA, NA, NA, NA, NA, NA, "tan", "darkred", "pink", "darkred", "purple", "darkred"),
  stringsAsFactors = FALSE
)

# Extract unique colors for file names
colors <- unique(c(gene_module_colors$clade4_Color[!is.na(gene_module_colors$clade4_Color)],
                   gene_module_colors$clade1_Color[!is.na(gene_module_colors$clade1_Color)]))

# Create a mapping of colors to file names
color_file_mapping <- list(
  yellow = "zScore_MEyellow_0_6_df_0.05.csv",
  red = "zScore_MEred_0_6_df_0.05.csv",
  greenyellow = "zScore_MEgreenyellow_0_6_df_0.05.csv",
  tan = "zScore_MEtan_0_6_df_0.05.csv",
  darkred = "zScore_MEdarkred_0_6_df_0.05.csv",
  pink = "zScore_MEpink_0_6_df_0.05.csv",
  purple = "zScore_MEpurple_0_6_df_0.05.csv"
  
)

# Function to read data, transform, select columns, and return
process_data <- function(file_path, genes_of_interest) {
  df <- read_csv(file_path)
  df <- transform(df, Color = Color.x)  # Create the Color column
  
  # Select only the desired columns. Handle missing columns gracefully.
  selected_columns <- c("GeneID", "Color.x", "gid", "cluster", "ReplicateGroup", "AvgExprs", "TCavg", "zScore", "TCsd")
  df_selected <- df %>%
    select(any_of(selected_columns)) %>%
    filter(GeneID %in% genes_of_interest)  # Filter for specified genes
  
  return(df_selected)
}

# Read and process each color dataset based on the mapping
genes_of_interest_clade4 <- gene_module_colors$Gene[grepl("_1$", gene_module_colors$Gene)]
genes_of_interest_clade1 <- gene_module_colors$Gene[grepl("_11$", gene_module_colors$Gene)]

# Process data according to the colors
MEyellow_0_6_df <- process_data(color_file_mapping[["yellow"]], genes_of_interest_clade4)
MEred_0_6_df <- process_data(color_file_mapping[["red"]], genes_of_interest_clade4)
MEgreenyellow_0_6_df <- process_data(color_file_mapping[["greenyellow"]], genes_of_interest_clade4)
MEtan_0_6_df <- process_data(color_file_mapping[["tan"]], genes_of_interest_clade1)
MEdarkred_0_6_df <- process_data(color_file_mapping[["darkred"]], genes_of_interest_clade1)
MEpink_0_6_df <- process_data(color_file_mapping[["pink"]], genes_of_interest_clade1)
MEpurple_0_6_df <- process_data(color_file_mapping[["purple"]], genes_of_interest_clade1)
# Bind all data frames
df_combined <- bind_rows(
  MEyellow_0_6_df,
  MEred_0_6_df,
  MEgreenyellow_0_6_df,
  MEtan_0_6_df,
  MEdarkred_0_6_df,
  MEpink_0_6_df,
  MEpurple_0_6_df
)

# Print the column names of the combined data frame to verify
print(colnames(df_combined))

# Ensure ReplicateGroup is a factor
df_combined$ReplicateGroup <- factor(df_combined$ReplicateGroup, levels = unique(df_combined$ReplicateGroup))

# Separate data for clade 2 and clade 5
df_clade1 <- df_combined %>% filter(Color.x %in% gene_module_colors$clade1_Color)
df_clade4 <- df_combined %>% filter(Color.x %in% gene_module_colors$clade4_Color)


# Load necessary library
library(dplyr)

# Remove duplicate rows from df_clade1
df_clade1_unique <- df_clade1 %>% distinct()

# If you want to keep it in the original df_clade1 variable
df_clade1 <- df_clade1 %>% distinct()

df <- df_clade1

# Assuming your data frame is named 'df_summary'
# Step 1: Summarize the data to get the mean Z score and standard deviation
mean_z_scores <- df %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup()



p <- ggplot(mean_z_scores, aes(x = ReplicateGroup, y = mean_zScore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore), fill = "blue", alpha = 0.2) +
  labs(title = "Six Genes within Clade 1",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )
p



df2 <- df_clade4

# Assuming your data frame is named 'df_summary'
# Step 1: Summarize the data to get the mean Z score and standard deviation
mean_z_scores2 <- df2 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup()



p2 <- ggplot(mean_z_scores2, aes(x = ReplicateGroup, y = mean_zScore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore), fill = "purple", alpha = 0.2) +
  labs(title = "Six Genes within Clade 4",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )
p2


# Summarize the data for Clade 2
mean_z_scores_clade1 <- df_clade1 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Clade = "Clade 1")

# Summarize the data for Clade 5
mean_z_scores_clade4 <- df_clade4 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Clade = "Clade 4")


# Combine the summaries into one data frame
mean_z_scores_combined <- bind_rows(mean_z_scores_clade1, mean_z_scores_clade4)

# Plot both datasets together
p <- ggplot(mean_z_scores_combined, aes(x = ReplicateGroup, y = mean_zScore, group = Clade, color = Clade)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore, fill = Clade), alpha = 0.2) +
  labs(title = "Mean  zScores for Clade 1 and Clade 4 of Six Genes",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  scale_color_manual(values = c("Clade 1" = "blue", "Clade 4" = "purple")) +  # Set line colors
  scale_fill_manual(values = c("Clade 1" = "blue", "Clade 4" = "purple")) +  # Set ribbon colors
  theme(
    axis.title = element_text(size = 14, face = "bold"),       # Axis titles
    axis.text = element_text(size = 12, face = "bold"),        # Axis text
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5)  # Plot title (centered)
  )

# Print the combined plot
print(p)
##############################clade3 and clade2



# Create a data frame for specified genes and their module colors for clade 2 and clade 5
# Create a data frame for specified genes and their module colors for clade 2 and clade 5
gene_module_colors <- data.frame(
  Gene = c("AT1G03130_1", "AT1G13245_1", "AT1G29910_1", "AT1G29930_1", "AT1G61520_1", 
           "AT2G34420_1", "AT2G46790_1", "AT3G54890_1", "AT3G59060_1", "AT3G61580_1", 
           "AT4G19170_1", "AT4G38850_1", "AT5G02810_1", "AT5G18030_1", "AT5G54270_1", 
           "AT5G62280_1", "AT5G64170_1",
           "AT1G03130_11", "AT1G13245_11", "AT1G29910_11", "AT1G29930_11", "AT1G61520_11", 
           "AT2G34420_11", "AT2G46790_11", "AT3G54890_11", "AT3G59060_11", "AT3G61580_11", 
           "AT4G19170_11", "AT4G38850_11", "AT5G02810_11", "AT5G18030_11", "AT5G54270_11", 
           "AT5G62280_11", "AT5G64170_11"),
  
  clade3_Color = c("brown", "brown", "brown", "brown", "brown", "brown", "salmon", "brown", 
                   "salmon", "brown", "salmon", "brown", "brown", "brown", "brown", "brown","salmon", 
                   NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA),
  
  clade2_Color = c(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
                   "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", 
                   "blue", "blue", "lightcyan", "lightcyan", "blue", "blue", "blue", "blue"),
  
  stringsAsFactors = FALSE
)
# Extract unique colors for file names
colors <- unique(c(gene_module_colors$clade3_Color[!is.na(gene_module_colors$clade3_Color)],
                   gene_module_colors$clade2_Color[!is.na(gene_module_colors$clade2_Color)]))

# Create a mapping of colors to file names
color_file_mapping <- list(
  brown = "zScore_MEbrown_0_6_df_0.05.csv",
  salmon = "zScore_MEsalmon_0_6_df_0.05.csv",
  blue = "zScore_MEblue_0_6_df_0.05.csv",
  tan = "zScore_MEtan_0_6_df_0.05.csv",
  lightcyan = "zScore_MElightcyan_0_6_df_0.05.csv"
)

# Function to read data, transform, select columns, and return
process_data <- function(file_path, genes_of_interest) {
  df <- read_csv(file_path)
  df <- transform(df, Color = Color.x)  # Create the Color column
  
  # Select only the desired columns. Handle missing columns gracefully.
  selected_columns <- c("GeneID", "Color.x", "gid", "cluster", "ReplicateGroup", "AvgExprs", "TCavg", "zScore", "TCsd")
  df_selected <- df %>%
    select(any_of(selected_columns)) %>%
    filter(GeneID %in% genes_of_interest)  # Filter for specified genes
  
  return(df_selected)
}

# Read and process each color dataset based on the mapping
genes_of_interest_clade3 <- gene_module_colors$Gene[grepl("_1$", gene_module_colors$Gene)]
genes_of_interest_clade2 <- gene_module_colors$Gene[grepl("_11$", gene_module_colors$Gene)]

# Process data according to the colors
MEbrown_0_6_df <- process_data(color_file_mapping[["brown"]], genes_of_interest_clade3)
MEsalmon_0_6_df <- process_data(color_file_mapping[["salmon"]], genes_of_interest_clade3)
MEblue_0_6_df <- process_data(color_file_mapping[["blue"]], genes_of_interest_clade2)
MElightcyan_0_6_df <- process_data(color_file_mapping[["lightcyan"]], genes_of_interest_clade2)

# Bind all data frames
df_combined <- bind_rows(
  MEbrown_0_6_df,
  MEsalmon_0_6_df,
  MEblue_0_6_df,
  MElightcyan_0_6_df
)

# Print the column names of the combined data frame to verify
print(colnames(df_combined))

# Ensure ReplicateGroup is a factor
df_combined$ReplicateGroup <- factor(df_combined$ReplicateGroup, levels = unique(df_combined$ReplicateGroup))

# Separate data for clade 2 and clade 5
df_clade2 <- df_combined %>% filter(Color.x %in% gene_module_colors$clade2_Color)
df_clade3 <- df_combined %>% filter(Color.x %in% gene_module_colors$clade3_Color)


# Load necessary library
library(dplyr)

# Remove duplicate rows from df_clade2
df_clade2_unique <- df_clade2 %>% distinct()

# If you want to keep it in the original df_clade2 variable
df_clade2 <- df_clade2 %>% distinct()

df <- df_clade2

# Assuming your data frame is named 'df_summary'
# Step 1: Summarize the data to get the mean Z score and standard deviation
mean_z_scores <- df %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup()



p <- ggplot(mean_z_scores, aes(x = ReplicateGroup, y = mean_zScore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore), fill = "red", alpha = 0.2) +
  labs(title = "Six Genes within Clade 2",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )
p



df2 <- df_clade3

# Assuming your data frame is named 'df_summary'
# Step 1: Summarize the data to get the mean Z score and standard deviation
mean_z_scores2 <- df2 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup()



p2 <- ggplot(mean_z_scores2, aes(x = ReplicateGroup, y = mean_zScore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore), fill = "darkgreen", alpha = 0.2) +
  labs(title = "Six Genes within Clade 3",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )
p2


# Summarize the data for Clade 2
mean_z_scores_clade2 <- df_clade2 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Clade = "Clade 2")

# Summarize the data for Clade 5
mean_z_scores_clade3 <- df_clade3 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Clade = "Clade 3")


# Combine the summaries into one data frame
mean_z_scores_combined <- bind_rows(mean_z_scores_clade2, mean_z_scores_clade3)

# Assuming you have already created the mean_z_scores_combined data frame

# Assuming you have already created the mean_z_scores_combined data frame

# Plot both datasets together
p <- ggplot(mean_z_scores_combined, aes(x = ReplicateGroup, y = mean_zScore, group = Clade, color = Clade)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore, fill = Clade), alpha = 0.2) +
  labs(title = "Mean  zScores for Clade 2 and Clade 3 of Seventeen Genes",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  scale_color_manual(values = c("Clade 2" = "red", "Clade 3" = "darkgreen")) +  # Set line colors
  scale_fill_manual(values = c("Clade 2" = "red", "Clade 3" = "darkgreen")) +  
  theme(
    axis.title = element_text(size = 14, face = "bold"),       # Axis titles
    axis.text = element_text(size = 12, face = "bold"),        # Axis text
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5)  # Plot title (centered)
  )
# Print the plot
print(p)

# Print the plot
print(p)

# Print the combined plot
print(p)




# Plot both datasets together
p <- ggplot(mean_z_scores_combined, aes(x = ReplicateGroup, y = mean_zScore, group = Clade, color = Clade)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore, fill = Clade), alpha = 0.2) +
  labs(title = "Mean  zScores for Clade 2 and Clade 3 of Seventeen Genes",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  scale_color_manual(values = c("Clade 2" = "red", "Clade 3" = "darkgreen")) +  # Set line colors
  scale_fill_manual(values = c("Clade 2" = "red", "Clade 3" = "darkgreen")) +  
  theme(
    axis.title = element_text(size = 14, face = "bold"),       # Axis titles
    axis.text = element_text(size = 12, face = "bold"),        # Axis text
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5)  # Plot title (centered)
  )


################clase3 vs clade5



# Create a data frame for specified genes and their module colors for clade 2 and clade 5
# Create a data frame for specified genes and their module colors for clade 2 and clade 5
gene_module_colors <- data.frame(
  Gene = c("AT1G14280_1", "AT1G16720_1", "AT1G73480_1", "AT1G73600_1", "AT2G30520_1", 
           "AT2G31380_1", "AT2G41250_1", "AT2G46830_1", "AT3G19630_1", "AT5G67030_1",
           "AT1G14280_11", "AT1G16720_11", "AT1G73480_11", "AT1G73600_11", "AT2G30520_11", 
           "AT2G31380_11", "AT2G41250_11", "AT2G46830_11", "AT3G19630_11", "AT5G67030_11"),
  
  clade5_Color = c("black", "turquoise", "black", "grey60", "black", "black", "black", "black", 
                   "turquoise", "turquoise", NA, NA, NA, NA, NA, NA, NA, NA, NA, NA),
  
  clade3_Color = c(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
                   "brown", "salmon", "brown", "brown", "brown", "brown", "salmon", "salmon", "brown", 
                   "salmon"),
  
  stringsAsFactors = FALSE
)
# Extract unique colors for file names
colors <- unique(c(gene_module_colors$clade5_Color[!is.na(gene_module_colors$clade5_Color)],
                   gene_module_colors$clade3_Color[!is.na(gene_module_colors$clade3_Color)]))

# Create a mapping of colors to file names
color_file_mapping <- list(
  black = "zScore_MEblack_0_6_df_0.05.csv",
  turquoise = "zScore_MEturquoise_0_6_df_0.05.csv",
  grey60 = "zScore_MEgrey60_0_6_df_0.05.csv",
  brown = "zScore_MEbrown_0_6_df_0.05.csv",
  salmon = "zScore_MEsalmon_0_6_df_0.05.csv"
)

# Function to read data, transform, select columns, and return
process_data <- function(file_path, genes_of_interest) {
  df <- read_csv(file_path)
  df <- transform(df, Color = Color.x)  # Create the Color column
  
  # Select only the desired columns. Handle missing columns gracefully.
  selected_columns <- c("GeneID", "Color.x", "gid", "cluster", "ReplicateGroup", "AvgExprs", "TCavg", "zScore", "TCsd")
  df_selected <- df %>%
    select(any_of(selected_columns)) %>%
    filter(GeneID %in% genes_of_interest)  # Filter for specified genes
  
  return(df_selected)
}

# Read and process each color dataset based on the mapping
genes_of_interest_clade5 <- gene_module_colors$Gene[grepl("_1$", gene_module_colors$Gene)]
genes_of_interest_clade3 <- gene_module_colors$Gene[grepl("_11$", gene_module_colors$Gene)]

# Process data according to the colors
MEblack_0_6_df <- process_data(color_file_mapping[["black"]], genes_of_interest_clade5)
MEturquoise_0_6_df <- process_data(color_file_mapping[["turquoise"]], genes_of_interest_clade5)
MEgrey60_0_6_df <- process_data(color_file_mapping[["grey60"]], genes_of_interest_clade5)
MEbrown_0_6_df <- process_data(color_file_mapping[["brown"]], genes_of_interest_clade3)
MEsalmon_0_6_df <- process_data(color_file_mapping[["salmon"]], genes_of_interest_clade3)


# Bind all data frames
df_combined <- bind_rows(
  MEblack_0_6_df,
  MEturquoise_0_6_df,
  MEgrey60_0_6_df,
  MEbrown_0_6_df,
  MEsalmon_0_6_df
)

# Print the column names of the combined data frame to verify
print(colnames(df_combined))

# Ensure ReplicateGroup is a factor
df_combined$ReplicateGroup <- factor(df_combined$ReplicateGroup, levels = unique(df_combined$ReplicateGroup))

# Separate data for clade 2 and clade 5
df_clade3 <- df_combined %>% filter(Color.x %in% gene_module_colors$clade3_Color)
df_clade5 <- df_combined %>% filter(Color.x %in% gene_module_colors$clade5_Color)

# Remove duplicate rows from df_clade3
df_clade5_unique <- df_clade5 %>% distinct()

# If you want to keep it in the original df_clade3 variable
df_clade5 <- df_clade5 %>% distinct()

# Load necessary library
library(dplyr)

# Remove duplicate rows from df_clade3
df_clade3_unique <- df_clade3 %>% distinct()

# If you want to keep it in the original df_clade3 variable
df_clade3 <- df_clade3 %>% distinct()

df <- df_clade3

# Assuming your data frame is named 'df_summary'
# Step 1: Summarize the data to get the mean Z score and standard deviation
mean_z_scores <- df %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup()



p <- ggplot(mean_z_scores, aes(x = ReplicateGroup, y = mean_zScore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore), fill = "darkgreen", alpha = 0.2) +
  labs(title = "Six Genes within Clade 3",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )
p



df2 <- df_clade5

# Assuming your data frame is named 'df_summary'
# Step 1: Summarize the data to get the mean Z score and standard deviation
mean_z_scores2 <- df2 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup()



p2 <- ggplot(mean_z_scores2, aes(x = ReplicateGroup, y = mean_zScore, group = 1)) +
  geom_line(color = "black") +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore), fill = "turquoise", alpha = 0.2) +
  labs(title = "Six Genes within Clade 5",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  
  # Increase font size
  theme(
    axis.title = element_text(size = 44, face = "bold"),       # Axis titles
    axis.text = element_text(size = 36, face = "bold"),        # Axis text
    plot.title = element_text(size = 36, face = "bold",  hjust = 0.5)  # Plot title (centered)
  )
p2


# Summarize the data for Clade 2
mean_z_scores_clade3 <- df_clade3 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Clade = "Clade 3")

# Summarize the data for Clade 5
mean_z_scores_clade5 <- df_clade5 %>%
  group_by(ReplicateGroup) %>%
  summarise(mean_zScore = mean(zScore, na.rm = TRUE),
            sd_zScore = sd(zScore, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Clade = "Clade 5")


# Combine the summaries into one data frame
mean_z_scores_combined <- bind_rows(mean_z_scores_clade3, mean_z_scores_clade5)

# Plot both datasets together
p <- ggplot(mean_z_scores_combined, aes(x = ReplicateGroup, y = mean_zScore, group = Clade, color = Clade)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_zScore - sd_zScore, ymax = mean_zScore + sd_zScore, fill = Clade), alpha = 0.2) +
  labs(title = "Mean  zScores for Clade 3 and Clade 5 of Ten Genes",
       x = "Replicate Group (Time Point)",
       y = "Average Z Score") +
  theme_minimal() +
  scale_color_manual(values = c("Clade 3" = "darkgreen", "Clade 5" = "turquoise")) +  # Set line colors
  scale_fill_manual(values = c("Clade 3" = "darkgreen", "Clade 5" = "turquoise")) +  # Set ribbon colors
  theme(
    axis.title = element_text(size = 14, face = "bold"),       # Axis titles
    axis.text = element_text(size = 12, face = "bold"),        # Axis text
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5)  # Plot title (centered)
  )

# Print the combined plot
print(p)

#######################################################


